---
title: "Prospective Memory, Metamemory, Depression"
output: 
  html_notebook:
    toc: yes
  html_document:
    toc: yes
    df_print: paged
---

# Data preparation--------------------------------------------------------------

# Using SQL to combine datasets and extract demographic info from screener
```{r}
#install.packages("readxl")  
#install.packages("sqldf")   
#install.packages("openxlsx") 

library(readxl)
library(sqldf)
library(openxlsx)

# Load the participant and screener files
participants <- read_excel("/Users/mickey.rice/Desktop/Dissertation/PMD/ActualParticipants.xlsx")
screener <- read_excel("/Users/mickey.rice/Desktop/Dissertation/PMD/Screener.xlsx")

query <- "
  SELECT p.*, 
         s.[Q413_1] as ADHD1,
         s.[Q414_1] as ADHD2,
         s.[Q415_1] as ADHD3,
         s.[Q416_1] as ADHD4,
         s.[Q417_1] as ADHD5,
         s.[Q418_1] as ADHD6,
         s.[Q1.52] as SES1,
         s.[Q1.53q] as SES2
  FROM participants p
  JOIN screener s
  ON p.ID = s.ID
"

# Run the SQL query to combine the data
combined_data <- sqldf(query)

# View the combined data
head(combined_data)

# Save to a new Excel file
write.xlsx(combined_data, "/Users/mickey.rice/Desktop/combined_data.xlsx")

```

# Add demographics info to data set with variables of interest

# Load Data 
```{r}
df <- read_excel("/Users/mickey.rice/Desktop/Dissertation/PMD/pmd_data.xlsx")
```

# Combine data
```{r}
columns_to_add <- combined_data[, c("ID_number", "Gender", "Race", "Age", "Ethnicity",
                                    "Handedness", "ADHD1", "ADHD2", "ADHD3", "ADHD4",
                                    "ADHD5", "ADHD6", "SES1", "SES2")]

PMD <- merge(df, columns_to_add, by = "ID_number")
```

# Add ADHD columns and SES columns
```{r}
library(dplyr)

PMD$ADHD1 <- as.numeric(PMD$ADHD1)
PMD$ADHD2 <- as.numeric(PMD$ADHD2)
PMD$ADHD3 <- as.numeric(PMD$ADHD3)
PMD$ADHD4 <- as.numeric(PMD$ADHD4)
PMD$ADHD5 <- as.numeric(PMD$ADHD5)
PMD$ADHD6 <- as.numeric(PMD$ADHD6)

# Add a new column for the total ADHD scores
PMD <- PMD %>%
  mutate(ADHD = ADHD1 + ADHD2 + ADHD3 + ADHD4 + ADHD5 + ADHD6)

library(readr)

# Extract numeric part of the SES columns
PMD$SES1 <- parse_number(PMD$SES1)
PMD$SES2 <- parse_number(PMD$SES2)

# Average together SES1 and SES2
PMD <- PMD %>%
  mutate(avgpared = rowMeans(across(c(SES1, SES2)), na.rm = TRUE))
```

# Load primary libaries for analyses
```{r}
library(psych)
library(tidyverse)
library(apaTables)
library(ggplot2)
library(mediation)
library(interactions)
library(jtools)
library(rlang)
```

```{r}
describe(PMD)
```

# Recode gender to be numeric
```{r}
PMD$Gender1<- 0
PMD$Gender1<-ifelse(PMD$Gender=="Male", 0, 
                    ifelse(PMD$Gender=="Female", 1, 2))
```


# Check to see if there is missing data
```{r}
any_missing <- any(is.na(PMD))
print(any_missing)
```

```{r}
library(naniar)
# Visualize missing data pattern
gg_miss_var(PMD)
```

# Fill missing values for Race
# Missing values
```{r}
# Replace missing Race values with "Do not wish to respond"
PMD$Race[is.na(PMD$Race)] <- "Do not wish to respond"
```

## Centering the variables for an interaction
```{r}
## centering the variable - most important for interaction
PHQ9 <- PMD$PHQ9
mean_PHQ9 <- mean(PHQ9)
PHQ9_c <- PHQ9 - mean_PHQ9
PMD$PHQ9_c <- PHQ9_c

CESD <- PMD$CESD
mean_CESD <- mean(CESD)
CESD_c <- CESD - mean_CESD
PMD$CESD_c <- CESD_c

DASS <- PMD$DASS
mean_DASS <- mean(DASS)
DASS_c <- DASS - mean_DASS
PMD$DASS_c <- DASS_c

PRMQ1 <- PMD$PRMQ1
mean_PRMQ1 <- mean(PRMQ1)
PRMQ1_c <- PRMQ1 - mean_PRMQ1
PMD$PRMQ1_c <- PRMQ1_c

Confidence <- PMD$Confidence
mean_Confidence <- mean(Confidence)
Confidence_c <- Confidence - mean_Confidence
PMD$Confidence_c <- Confidence_c

JOL <- PMD$JOL
mean_JOL <- mean(JOL)
JOL_c <- JOL - mean_JOL
PMD$JOL_c <- JOL_c


N300 <- PMD$N300
mean_N300 <- mean(N300)
N300_c <- N300 - mean_N300
PMD$N300_c <- N300_c

PP <- PMD$PP
mean_PP <- mean(PP)
PP_c <- PP - mean_PP
PMD$PP_c <- PP_c
```

# Analysis----------------------------------------------------------------------

# Regression main effects-------------------------------------------------------

## Regression: Depression predicting Accuracy controlling for age and gender
```{r}
fit1 <- lm(scale(Accuracy) ~ scale(PHQ9) + Age + Gender1, data = PMD)
summary(fit1)

fit2 <- lm(scale(Accuracy) ~ scale(CESD) + Age + Gender1, data = PMD)
summary(fit2)
```

## Regression: Depression predicting RT controlling for age and gender
```{r}
fit1 <- lm(scale(RT) ~ scale(PHQ9) + Gender1 + Age, data = PMD)
summary(fit1)

fit2 <- lm(scale(RT) ~ scale(CESD) + Gender1 + Age, data = PMD)
summary(fit2)
```

## Regression: Depression predicting metamemory controlling for age and gender
```{r}
fit1 <- lm(scale(PRMQ1) ~ scale(PHQ9) + Gender1 + Age, data = PMD)
summary(fit1)

fit2 <- lm(scale(Confidence) ~ scale(PHQ9) + Gender1 + Age, data = PMD)
summary(fit2)

fit3 <- lm(scale(JOL) ~ scale(PHQ9) + Gender1 + Age, data = PMD)
summary(fit3)

fit4 <- lm(scale(PRMQ1) ~ scale(CESD) + Gender1 + Age, data = PMD)
summary(fit4)

fit5 <- lm(scale(Confidence) ~ scale(CESD) + Gender1 + Age, data = PMD)
summary(fit5)

fit6 <- lm(scale(JOL) ~ scale(CESD) + Gender1 + Age, data = PMD)
summary(fit6)
```

## Regression: Depression predicting N300 controlling for age and gender
```{r}
fit1 <- lm(scale(N300) ~ scale(PHQ9) + Age + Gender1, data = PMD)
summary(fit1)

fit2 <- lm(scale(N300) ~ scale(CESD) + Age + Gender1, data = PMD)
summary(fit2)

```

## Regression: Depression predicting PP controlling for age and gender
```{r}
fit1 <- lm(scale(PP) ~ scale(PHQ9) + Age + Gender1, data = PMD)
summary(fit1)

fit2 <- lm(scale(PP) ~ scale(CESD) + Age + Gender1, data = PMD)
summary(fit2)
```


## Regression: N300 predicting Accuracy and RT controlling for age and gender
```{r}
fit1 <- lm(scale(Accuracy) ~ scale(N300) + Gender1 + Age, data = PMD)
summary(fit1)

fit2 <- lm(scale(RT) ~ scale(N300) + Gender1 + Age, data = PMD)
summary(fit2)
```

## Regression: PP predicting Accuracy and RT controlling for age and gender
```{r}
fit1 <- lm(scale(Accuracy) ~ scale(PP) + Gender1 + Age, data = PMD)
summary(fit1)

fit2 <- lm(scale(RT) ~ scale(PP) + Gender1 + Age, data = PMD)
summary(fit2)
```

# Regression: Metamemtory predicting Accuracy controlling for age and gender
```{r}
fit1 <- lm(scale(Accuracy) ~ scale(PRMQ1) + Age + Gender1, data = PMD)
summary(fit1)

fit2 <- lm(scale(Accuracy) ~ scale(Confidence) + Age + Gender1, data = PMD)
summary(fit2)

fit3 <- lm(scale(Accuracy) ~ scale(JOL) + Age + Gender1, data = PMD)
summary(fit3)
```

# Regression: Metamemtory predicting RT controlling for age and gender
```{r}
fit1 <- lm(scale(RT) ~ scale(PRMQ1) + Age + Gender1, data = PMD)
summary(fit1)

fit2 <- lm(scale(RT) ~ scale(Confidence) + Age + Gender1, data = PMD)
summary(fit2)

fit3 <- lm(scale(RT) ~ scale(JOL) + Age + Gender1, data = PMD)
summary(fit3)
```

## Effect sizes
```{r}
DVs <- c("Accuracy", "RT", "N300", "PP", "PRMQ1", "Confidence", "JOL")
IVs <- c("PHQ9", "CESD", "PRMQ1", "Confidence", "JOL", "N300", "PP")

# Create a list to store the results
results <- list()

# Loop through DVs and IVs to calculate partial R-squared
for (dv in DVs) {
  for (iv in IVs) {
    # Skip if the DV and IV are the same
    if (dv == iv) {
      next
    }
    
    # Full model (with the IV)
    full_model <- lm(as.formula(paste(dv, "~", iv, "+ Age + Gender1")), data = PMD)
    
    # Reduced model (without the IV)
    reduced_model <- lm(as.formula(paste(dv, "~", "Age + Gender1")), data = PMD)
    
    # R-squared for the full model
    r_squared_full <- summary(full_model)$r.squared
    
    # R-squared for the reduced model
    r_squared_reduced <- summary(reduced_model)$r.squared
    
    # Partial R-squared
    partial_r_squared <- r_squared_full - r_squared_reduced
    
    # Store the result
    results[[paste(dv, iv, sep = "_")]] <- partial_r_squared
  }
}

# Convert results into a data frame
results_df <- data.frame(
  Model = names(results),
  Partial_R_Squared = unlist(results)
)

# Write results to an Excel file
write.xlsx(results_df, "Partial_R_Squared_Results.xlsx", rowNames = FALSE)

print(results_df)

```

# Mediation --------------------------------------------------------------------
## Mediatior: PRMQ1 (based on regression main effects)
### IV: PHQ9
```{r}
model.M <- lm(PRMQ1 ~ PHQ9 + Gender1 + Age, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + PHQ9 + Gender1 + Age, data = PMD)
results_nomod <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "PHQ9", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(results_nomod)
```

### IV: CESD
```{r}
model.M <- lm(PRMQ1 ~ CESD + Gender1 + Age, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + CESD + Gender1 + Age, data =PMD)
results_nomod <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "CESD", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(results_nomod)
```

# Interactions -----------------------------------------------------------------
## ERP components (N300 and PP) moderating the relationship between depression and PM accuracy
```{r}
lm1 <- lm(Accuracy ~ PHQ9_c * N300_c + Gender1 + Age, PMD)
summary(lm1)

lm2 <- lm(Accuracy ~ CESD_c * N300_c + Gender1 + Age, PMD)
summary(lm2)

lm3 <- lm(Accuracy ~ PHQ9_c * PP_c + Gender1 + Age, PMD)
summary(lm3)

lm4 <- lm(Accuracy ~ CESD_c * PP_c + Gender1 + Age, PMD)
summary(lm4)
```
## Simple slopes
### IV: PHQ9 * N300
```{r}
fitInt <- lm(Accuracy ~ PHQ9_c * N300_c + Gender1 + Age, data = PMD)
summary(fitInt)

sim_slopes(
  fitInt,
  PHQ9_c,
  N300_c,
  mod2 = NULL,
  modx.values = NULL,
  mod2.values = NULL,
  centered = "none",
  data = PMD,
  cond.int = FALSE,
  johnson_neyman = TRUE,
  jnplot = FALSE,
  jnalpha = 0.05,
  robust = FALSE,
  digits = getOption("jtools-digits", default = 2),
  pvals = TRUE,
  confint = FALSE,
  ci.width = 0.95)
```

### IV:CESD * N300
```{r}
fitInt <- lm(Accuracy ~ CESD_c * N300_c + Gender1 + Age, data = PMD)
summary(fitInt)

sim_slopes(
  fitInt,
  CESD_c,
  N300_c,
  mod2 = NULL,
  modx.values = NULL,
  mod2.values = NULL,
  centered = "none",
  data = PMD,
  cond.int = FALSE,
  johnson_neyman = TRUE,
  jnplot = FALSE,
  jnalpha = 0.05,
  robust = FALSE,
  digits = getOption("jtools-digits", default = 2),
  pvals = TRUE,
  confint = FALSE,
  ci.width = 0.95)
```
## Interaction plots
```{r}
fitInt <- lm(Accuracy ~ PHQ9_c * N300_c + Gender1 + Age, data = PMD)

plot <- interact_plot(fitInt, pred = PHQ9_c, modx = N300_c, 
               plot.points = TRUE,    # To show individual data points
               interval = TRUE,       # To include confidence intervals
               colors = "Set1")  


# Customize the axis titles
plot <- plot + 
  labs(x = "PHQ-9 Scores",  
       y = "Accuracy",
       color = "N300_c") 

print(plot)

ggsave("PHQ9*N300_Accuracy", path = '/Users/mickey.rice/Desktop/', bg="white", width = 5, height = 5, device='jpeg', dpi= 700)
       
```

```{r}
fitInt <- lm(Accuracy ~ CESD_c * N300_c + Gender1 + Age, data = PMD)

plot <- interact_plot(fitInt, pred = CESD_c, modx = N300_c, 
               plot.points = TRUE,    # To show individual data points
               interval = TRUE,       # To include confidence intervals
               colors = "Set1")       


# Customize the axis titles
plot <- plot + 
  labs(x = "CES-D Scores",  
       y = "Accuracy",
       color = "N300_c") 

print(plot)

ggsave("CESD*N300_Accuracy", path = '/Users/mickey.rice/Desktop/', bg="white", width = 5, height = 5, device='jpeg', dpi= 700)
       
```

# Moderated Mediation ----------------------------------------------------------
## Moderator on the direct pathway: N300 moderating depression -> accuracy in the mediation model

### PHQ9
```{r}
## Remove age as a covariate to resolve issues with multicollinearity/over fitting 

model.M <- lm(PRMQ1 ~ PHQ9_c + Gender1, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + PHQ9_c * N300_c + Gender1, data =PMD)
results <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "PHQ9_c", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(results)
```

### CESD
```{r}
model.M <- lm(PRMQ1 ~ CESD_c + Gender1, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + CESD_c * N300_c + Gender1, data =PMD)
results <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "CESD_c", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(results)
```

## Check conditional indirect effects (at 3 levels of the moderator, N300)
### PHQ9
```{r}
# Define values for the moderator (W) at mean, mean + 1 SD, and mean - 1 SD
mean_W <- mean(PMD$N300_c, na.rm = TRUE)
sd_W <- sd(PMD$N300_c, na.rm = TRUE)

W_levels <- c(mean_W, mean_W + sd_W, mean_W - sd_W)

# List to store results for each level of W
results <- list()

for (i in 1:length(W_levels)) {
  # Create a copy of the data with N300_c set to the specific level
  PMD_subset <- PMD
  PMD_subset$N300_c <- W_levels[i]
  
  # Define the mediator and outcome models
  mediator_model <- lm(PRMQ1 ~ PHQ9_c + Gender1, data = PMD_subset)
  outcome_model <- lm(Accuracy ~ PRMQ1 + PHQ9_c * N300_c + Gender1, data = PMD_subset)
  
  # Run the mediation analysis
  mediation_results <- mediation::mediate(mediator_model, 
                               outcome_model, 
                               treat = "PHQ9_c", 
                               mediator = "PRMQ1", 
                               boot = TRUE, sims = 10000)
  
  # Store the mediation results for each level
  results[[paste0("N300_c_", i)]] <- summary(mediation_results)
}

# Display the results for each level of W
results
```

### CESD
```{r}
# Define values for the moderator (W) at mean, mean + 1 SD, and mean - 1 SD
mean_W <- mean(PMD$N300_c, na.rm = TRUE)
sd_W <- sd(PMD$N300_c, na.rm = TRUE)

W_levels <- c(mean_W, mean_W + sd_W, mean_W - sd_W)

# List to store results for each level of W
results <- list()

for (i in 1:length(W_levels)) {
  # Create a copy of the data with N300_c set to the specific level
  PMD_subset <- PMD
  PMD_subset$N300_c <- W_levels[i]
  
  # Define the mediator and outcome models
  mediator_model <- lm(PRMQ1 ~ CESD_c + Gender1, data = PMD_subset)
  outcome_model <- lm(Accuracy ~ PRMQ1 + CESD_c * N300_c + Gender1, data = PMD_subset)
  
  # Run the mediation analysis
  mediation_results <- mediation::mediate(mediator_model, 
                               outcome_model, 
                               treat = "CESD_c", 
                               mediator = "PRMQ1", 
                               boot = TRUE, sims = 10000)
  
  # Store the mediation results for each level
  results[[paste0("N300_c_", i)]] <- summary(mediation_results)
}

# Display the results for each level of W
results
```

# Interpretation
Final findings: Depression (PHQ9 and CESD) negatively predicts PM accuracy. This 
relationship is strengthened by a more negative N300 amplitude, which represents 
larger cue detection neural responses. In other words, larder cue detection 
responses enhance depression's negative role in PM accuracy. 
Metamemory beliefs (PRMQ1) fully mediate the relationship between depression and 
PM accuracy. When evaluating the moderated mediation, metamemory's role as a 
mediator is resilient to different levels of N300 amplitudes (i.e., cue detection
responses). 
Both the mediation and moderation effects exist independently. 

# Sensitivity analyses for main effects ----------------------------------------

## Additional covariates for metamemory -> PM and ERPs 
## parental education, ADHD, motivation, sleepiness, sleep hours
```{r}
library(openxlsx)

# List of dependent variables
dependent_vars <- c('Accuracy', 'RT', 'PP', 'N300')

# Independent variables to be tested sequentially
selected_columns <- c('PRMQ1', 'Confidence', 'JOL')

# List of additional controls
additional_controls <- list(
  SES = "PMD$avgpared",       # Socioeconomic status
  ADHD = "PMD$ADHD",     # ADHD symptoms
  Motivation = "PMD$Motivation", # motivation score
  Sleepiness = "PMD$Sleepiness", # Sleepiness score
  HrsSleep = "PMD$HrsSleep" # Hours of sleep the night before
)

# Initialize the results dataframe
results <- data.frame(Dependent_Variable = character(), 
                      Independent_Variable = character(), 
                      Control_Variable = character(),
                      Estimate = numeric(), 
                      P_Value = numeric(), 
                      stringsAsFactors = FALSE)

# Outer loop for dependent variables
for (dep_var in dependent_vars) {
  
  # Inner loop for independent variables (tested sequentially)
  for (col in selected_columns) {
    
    # Loop for additional controls
    for (control_name in names(additional_controls)) {
      control_var <- additional_controls[[control_name]]
      
      # Construct the formula for each model
      formula_str <- paste("PMD$", dep_var, " ~ PMD$", col, " + PMD$Gender1 + PMD$Age + ", control_var, sep = "")
      
      # Run the linear model
      lm1 <- lm(as.formula(formula_str), data = PMD)
      summary_lm1 <- summary(lm1)
      
      # Extract estimate and p-value for the variable of interest (col)
      estimate <- summary_lm1$coefficients[2, 1]  # 2nd row, 1st column (estimate)
      p_value <- summary_lm1$coefficients[2, 4]   # 2nd row, 4th column (p-value)
      
      # Store the result in the results dataframe
      results <- rbind(results, data.frame(Dependent_Variable = dep_var, 
                                           Independent_Variable = col, 
                                           Control_Variable = control_name,
                                           Estimate = estimate, 
                                           P_Value = p_value))
    }
  }
}

# Write the results to an Excel file
write.xlsx(results, file = "/Users/mickey.rice/Desktop/results1.xlsx", rowNames = FALSE)
```

## Additional covariates for depression and ERPS -> PM 
## parental education, ADHD, motivation, sleepiness, sleep hours, anxiety, positive and negative affect
```{r}
library(openxlsx)

# List of dependent variables
dependent_vars <- c('Accuracy', 'RT')

# Independent variables to be tested sequentially
selected_columns <- c('PHQ9', 'CESD', 'PP', 'N300')

# List of additional controls
additional_controls <- list(
  SES = "PMD$avgpared",       # Socioeconomic status
  ADHD = "PMD$ADHD",     # ADHD symptoms
  Motivation = "PMD$Motivation", # motivation score
  Sleepiness = "PMD$Sleepiness", # Sleepiness score
  HrsSleep = "PMD$HrsSleep", # Hours of sleep the night before
    Anxiety = 'STAIS', # State anxiety levels
  PositiveAff = 'PosAff', # positive affect
  NegativeAff = 'NegAff' # negative affect
)

# Initialize the results dataframe
results <- data.frame(Dependent_Variable = character(), 
                      Independent_Variable = character(), 
                      Control_Variable = character(),
                      Estimate = numeric(), 
                      P_Value = numeric(), 
                      stringsAsFactors = FALSE)

# Outer loop for dependent variables
for (dep_var in dependent_vars) {
  
  # Inner loop for independent variables (tested sequentially)
  for (col in selected_columns) {
    
    # Loop for additional controls
    for (control_name in names(additional_controls)) {
      control_var <- additional_controls[[control_name]]
      
      # Construct the formula for each model
      formula_str <- paste("PMD$", dep_var, " ~ PMD$", col, " + PMD$Gender1 + PMD$Age + ", control_var, sep = "")
      
      # Run the linear model
      lm1 <- lm(as.formula(formula_str), data = PMD)
      summary_lm1 <- summary(lm1)
      
      # Extract estimate and p-value for the variable of interest (col)
      estimate <- summary_lm1$coefficients[2, 1]  # 2nd row, 1st column (estimate)
      p_value <- summary_lm1$coefficients[2, 4]   # 2nd row, 4th column (p-value)
      
      # Store the result in the results dataframe
      results <- rbind(results, data.frame(Dependent_Variable = dep_var, 
                                           Independent_Variable = col, 
                                           Control_Variable = control_name,
                                           Estimate = estimate, 
                                           P_Value = p_value))
    }
  }
}

# Write the results to an Excel file
write.xlsx(results, file = "/Users/mickey.rice/Desktop/results2.xlsx", rowNames = FALSE)
```

