---
title: "Moderated Mediation"
output: 
  html_notebook:
    toc: yes
  html_document:
    toc: yes
    df_print: paged
---

Created by Mickey Rice
November 7th, 2024

# Load Libaries 
```{r}
#library(car)
#library(lsr)
#library(MBESS)
library(psych)
library(tidyverse)
library(apaTables)
library(mediation)
library(interactions)
library(jtools)
library(rlang)
```

# Load Data 
```{r}
PMD <- read_csv("PMD.csv")
```
# Recode variables 
```{r}

PMD$Sex1<- 0
PMD$Sex1<-ifelse(PMD$Gender=="Male",-1, 1)


PMD$Gender1<- 0
PMD$Gender1<-ifelse(PMD$Gender=="Male", 0, 
                    ifelse(PMD$Gender=="Female", 1, 2))

## Explaining code : PM$Gender1<- 0 creates the new variable titled Gender1 
## PM$Gender1<-ifelse(PM$Gender ==“Male”,0 , ifelse(PM$Gender=="Female", 1, 2))) says “if the Gender is male, they will be 0, if Gender is female, they will be 1, if Gender is anything else it will be 2" 
```

## Centering the variables for an interaction
```{r}
## centering the variable - most important for interaction
PHQ9 <- PMD$PHQ9
mean_PHQ9 <- mean(PHQ9)
PHQ9_c <- PHQ9 - mean_PHQ9
PMD$PHQ9_c <- PHQ9_c

CESD <- PMD$CESD
mean_CESD <- mean(CESD)
CESD_c <- CESD - mean_CESD
PMD$CESD_c <- CESD_c

DASS <- PMD$DASS
mean_DASS <- mean(DASS)
DASS_c <- DASS - mean_DASS
PMD$DASS_c <- DASS_c

PRMQ1 <- PMD$PRMQ1
mean_PRMQ1 <- mean(PRMQ1)
PRMQ1_c <- PRMQ1 - mean_PRMQ1
PMD$PRMQ1_c <- PRMQ1_c

Confidence <- PMD$Confidence
mean_Confidence <- mean(Confidence)
Confidence_c <- Confidence - mean_Confidence
PMD$Confidence_c <- Confidence_c

JOL <- PMD$JOL
mean_JOL <- mean(JOL)
JOL_c <- JOL - mean_JOL
PMD$JOL_c <- JOL_c


N300 <- PMD$N300
mean_N300 <- mean(N300)
N300_c <- N300 - mean_N300
PMD$N300_c <- N300_c

PP <- PMD$PP
mean_PP <- mean(PP)
PP_c <- PP - mean_PP
PMD$PP_c <- PP_c

fitInt <- lm(Accuracy ~ N300_c * PRMQ1_c + Gender1 + Age, data = PMD)
summary(fitInt)

# PM$Gender1_f <- as.factor(PM$Gender1)

# contrasts(PM$Gender1_f) <- contr.helmert(n = 3)

```

# Run regression main effects without controlling for age

## PHQ9
```{r}
lm <- lm(scale(Accuracy) ~ scale(PHQ9) + Gender1, PMD)
summary(lm)

lm <- lm(scale(Accuracy) ~ scale(PRMQ1) + Gender1, PMD)
summary(lm)

lm <- lm(scale(PRMQ1) ~ scale(PHQ9) + Gender1, PMD)
summary(lm)
```

## CESD
```{r}
lm <- lm(scale(Accuracy) ~ scale(CESD) + Gender1, PMD)
summary(lm)

lm <- lm(scale(Accuracy) ~ scale(PRMQ1) + Gender1, PMD)
summary(lm)

lm <- lm(scale(PRMQ1) ~ scale(CESD) + Gender1, PMD)
summary(lm)

```

# Run interactions without controlling for age
```{r}
lm <- lm(Accuracy ~ PHQ9_c * N300_c + Gender1, PMD)
summary(lm)

lm <- lm(Accuracy ~ CESD_c * N300_c + Gender1, PMD)
summary(lm)
```

## Simple slopes
### PHQ9
```{r}
fitInt <- lm(Accuracy ~ PHQ9_c * N300_c + Gender1, data = PMD)
summary(fitInt)

sim_slopes(
  fitInt,
  PHQ9_c,
  N300_c,
  mod2 = NULL,
  modx.values = NULL,
  mod2.values = NULL,
  centered = "none",
  data = PMD,
  cond.int = FALSE,
  johnson_neyman = TRUE,
  jnplot = FALSE,
  jnalpha = 0.05,
  robust = FALSE,
  digits = getOption("jtools-digits", default = 2),
  pvals = TRUE,
  confint = FALSE,
  ci.width = 0.95)
```
### CESD
```{r}
fitInt <- lm(Accuracy ~ CESD_c * N300_c + Gender1, data = PMD)
summary(fitInt)

sim_slopes(
  fitInt,
  CESD_c,
  N300_c,
  mod2 = NULL,
  modx.values = NULL,
  mod2.values = NULL,
  centered = "none",
  data = PMD,
  cond.int = FALSE,
  johnson_neyman = TRUE,
  jnplot = FALSE,
  jnalpha = 0.05,
  robust = FALSE,
  digits = getOption("jtools-digits", default = 2),
  pvals = TRUE,
  confint = FALSE,
  ci.width = 0.95)
```

# Mediation without controlling for age

## PHQ9
```{r}
model.M <- lm(PRMQ1 ~ PHQ9 + Gender1, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + PHQ9 + Gender1, data =PMD)
results_nomod <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "PHQ9", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(results_nomod)
```
## Create APA formatted table
```{r}
# Extract effect estimates, confidence intervals, standard errors, and p-values
indirect_effect <- results_nomod$d0
indirect_ci <- c(results_nomod$d0.ci[1], results_nomod$d0.ci[2])
indirect_se <- sd(results_nomod$d0.sims)
indirect_p <- results_nomod$d0.p

direct_effect <- results_nomod$z0
direct_ci <- c(results_nomod$z0.ci[1], results_nomod$z0.ci[2])
direct_se <- sd(results_nomod$z0.sims)
direct_p <- results_nomod$z0.p

total_effect <- results_nomod$tau.coef
total_ci <- c(results_nomod$tau.ci[1], results_nomod$tau.ci[2])
total_se <- sd(results_nomod$tau.sims)
total_p <- results_nomod$tau.p

# Create data frame with all values
results_table <- data.frame(
  Effect = c("Indirect", "Direct", "Total"),
  Estimate = c(indirect_effect, direct_effect, total_effect),
  SE = c(indirect_se, direct_se, total_se),
  `CI Lower` = c(indirect_ci[1], direct_ci[1], total_ci[1]),
  `CI Upper` = c(indirect_ci[2], direct_ci[2], total_ci[2]),
  `p-value` = c(indirect_p, direct_p, total_p)
)

# install.packages("kableExtra")
# install.packages("officer")
library(officer)
library(kableExtra)

# Create APA-style table
results_table %>%
  kable("html", caption = "Mediation Analysis Results") %>%
  kable_styling(full_width = FALSE, position = "center") %>%
  add_header_above(c(" " = 1, "Estimate" = 1, "Standard Error" = 1, "95% Confidence Interval" = 2, " " = 1)) %>%
  column_spec(2, bold = TRUE) %>%
  footnote(general = "Estimates, standard errors, confidence intervals, and p-values for the indirect, direct, and total effects.",
           general_title = "Note: ")

library(officer)
library(kableExtra)

# Create APA-style table in HTML format
results_html_table <- results_table %>%
  kable("html", caption = "Model Results for PHQ-9 Relating to PM Accuracy via PM-related Metamemory  Beliefs (PRMQ) while controlling for only gender") %>%
  kable_styling(full_width = FALSE, position = "center") %>%
  add_header_above(c(" " = 1, "Standardized Beta" = 1, "Standard Error" = 1, "95% Confidence Interval" = 2, " " = 1)) %>%
  column_spec(2, bold = TRUE) %>%
  footnote(general = "Standardized Betas, standard errors, confidence intervals, and p-values for the indirect, direct, and total effects.",
           general_title = "Note: ")

# Create a new Word document
doc <- read_docx()

# Add the table to the Word document
doc <- doc %>%
  body_add_par("Model Results for PHQ-9 Relating to PM Accuracy via PM-related Metamemory  Beliefs (PRMQ) while controlling for only gender", style = "heading 1") %>%
  body_add_table(value = results_table, style = "table_template") %>%  # You can define a style template in Word if you prefer
  body_add_par("Note: Standardized Betas, standard errors, confidence intervals, and p-values for the indirect, direct, and total effects.", style = "Normal")

# Save the document
print(doc, target = "PHQ9_gender_Mediation_Analysis_Results.docx")

```

## CESD
```{r}
model.M <- lm(PRMQ1 ~ CESD + Gender1, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + CESD + Gender1, data =PMD)
results_nomod <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "CESD", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(results_nomod)
```
## Create APA formatted table
```{r}
# Extract effect estimates, confidence intervals, standard errors, and p-values
indirect_effect <- results_nomod$d0
indirect_ci <- c(results_nomod$d0.ci[1], results_nomod$d0.ci[2])
indirect_se <- sd(results_nomod$d0.sims)
indirect_p <- results_nomod$d0.p

direct_effect <- results_nomod$z0
direct_ci <- c(results_nomod$z0.ci[1], results_nomod$z0.ci[2])
direct_se <- sd(results_nomod$z0.sims)
direct_p <- results_nomod$z0.p

total_effect <- results_nomod$tau.coef
total_ci <- c(results_nomod$tau.ci[1], results_nomod$tau.ci[2])
total_se <- sd(results_nomod$tau.sims)
total_p <- results_nomod$tau.p

# Create data frame with all values
results_table <- data.frame(
  Effect = c("Indirect", "Direct", "Total"),
  Estimate = c(indirect_effect, direct_effect, total_effect),
  SE = c(indirect_se, direct_se, total_se),
  `CI Lower` = c(indirect_ci[1], direct_ci[1], total_ci[1]),
  `CI Upper` = c(indirect_ci[2], direct_ci[2], total_ci[2]),
  `p-value` = c(indirect_p, direct_p, total_p)
)

# install.packages("kableExtra")
# install.packages("officer")
library(officer)
library(kableExtra)

# Create APA-style table in HTML format
results_html_table <- results_table %>%
  kable("html", caption = "Model Results for CES-D Relating to PM Accuracy via PM-related Metamemory  Beliefs (PRMQ) while controlling for only gender") %>%
  kable_styling(full_width = FALSE, position = "center") %>%
  add_header_above(c(" " = 1, "Standardized Beta" = 1, "Standard Error" = 1, "95% Confidence Interval" = 2, " " = 1)) %>%
  column_spec(2, bold = TRUE) %>%
  footnote(general = "Standardized Betas, standard errors, confidence intervals, and p-values for the indirect, direct, and total effects.",
           general_title = "Note: ")

# Create a new Word document
doc <- read_docx()

# Add the table to the Word document
doc <- doc %>%
  body_add_par("Model Results for CES-D Relating to PM Accuracy via PM-related Metamemory  Beliefs (PRMQ) while controlling for only gender", style = "heading 1") %>%
  body_add_table(value = results_table, style = "table_template") %>%  # You can define a style template in Word if you prefer
  body_add_par("Note: Standardized Betas, standard errors, confidence intervals, and p-values for the indirect, direct, and total effects.", style = "Normal")

# Save the document
print(doc, target = "CESD_gender_Mediation_Analysis_Results.docx")

```




# Moderated mediation without controlling for age 
## PHQ9
```{r}
model.M <- lm(PRMQ1 ~ PHQ9_c + Gender1, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + PHQ9_c * N300_c + Gender1, data =PMD)
results <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "PHQ9_c", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(results)
```
## Create APA formatted table
```{r}
# Extract effect estimates, confidence intervals, standard errors, and p-values
indirect_effect <- results$d0
indirect_ci <- c(results$d0.ci[1], results$d0.ci[2])
indirect_se <- sd(results$d0.sims)
indirect_p <- results$d0.p

direct_effect <- results$z0
direct_ci <- c(results$z0.ci[1], results$z0.ci[2])
direct_se <- sd(results$z0.sims)
direct_p <- results$z0.p

total_effect <- results$tau.coef
total_ci <- c(results$tau.ci[1], results$tau.ci[2])
total_se <- sd(results$tau.sims)
total_p <- results$tau.p

# Create data frame with all values
results_table <- data.frame(
  Effect = c("Indirect", "Direct", "Total"),
  Estimate = c(indirect_effect, direct_effect, total_effect),
  SE = c(indirect_se, direct_se, total_se),
  `CI Lower` = c(indirect_ci[1], direct_ci[1], total_ci[1]),
  `CI Upper` = c(indirect_ci[2], direct_ci[2], total_ci[2]),
  `p-value` = c(indirect_p, direct_p, total_p)
)

# install.packages("kableExtra")
# install.packages("officer")
library(officer)
library(kableExtra)

# Create APA-style table in HTML format
results_html_table <- results_table %>%
  kable("html", caption = "Model Results for PHQ-9 Relating to PM Accuracy via PM-related Metamemory Beliefs (PRMQ) with Cue Detection as a Moderator while controlling for only gender") %>%
  kable_styling(full_width = FALSE, position = "center") %>%
  add_header_above(c(" " = 1, "Standardized Beta" = 1, "Standard Error" = 1, "95% Confidence Interval" = 2, " " = 1)) %>%
  column_spec(2, bold = TRUE) %>%
  footnote(general = "Standardized Betas, standard errors, confidence intervals, and p-values for the indirect, direct, and total effects.",
           general_title = "Note: ")

# Create a new Word document
doc <- read_docx()

# Add the table to the Word document
doc <- doc %>%
  body_add_par("Model Results for PHQ-9 Relating to PM Accuracy via PM-related Metamemory Beliefs (PRMQ) with Cue Detection as a Moderator while controlling for only gender", style = "heading 1") %>%
  body_add_table(value = results_table, style = "table_template") %>%  # You can define a style template in Word if you prefer
  body_add_par("Note: Standardized Betas, standard errors, confidence intervals, and p-values for the indirect, direct, and total effects.", style = "Normal")

# Save the document
print(doc, target = "PHQ9_gender_ModMediation_Analysis_Results.docx")

```


## CESD
```{r}
model.M <- lm(PRMQ1 ~ CESD_c + Gender1, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + CESD_c * N300_c + Gender1, data =PMD)
results <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "CESD_c", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(results)
```
## Create APA formatted table
```{r}
# Extract effect estimates, confidence intervals, standard errors, and p-values
indirect_effect <- results$d0
indirect_ci <- c(results$d0.ci[1], results$d0.ci[2])
indirect_se <- sd(results$d0.sims)
indirect_p <- results$d0.p

direct_effect <- results$z0
direct_ci <- c(results$z0.ci[1], results$z0.ci[2])
direct_se <- sd(results$z0.sims)
direct_p <- results$z0.p

total_effect <- results$tau.coef
total_ci <- c(results$tau.ci[1], results$tau.ci[2])
total_se <- sd(results$tau.sims)
total_p <- results$tau.p

# Create data frame with all values
results_table <- data.frame(
  Effect = c("Indirect", "Direct", "Total"),
  Estimate = c(indirect_effect, direct_effect, total_effect),
  SE = c(indirect_se, direct_se, total_se),
  `CI Lower` = c(indirect_ci[1], direct_ci[1], total_ci[1]),
  `CI Upper` = c(indirect_ci[2], direct_ci[2], total_ci[2]),
  `p-value` = c(indirect_p, direct_p, total_p)
)

# install.packages("kableExtra")
# install.packages("officer")
library(officer)
library(kableExtra)

# Create APA-style table in HTML format
results_html_table <- results_table %>%
  kable("html", caption = "Model Results for CES-D Relating to PM Accuracy via PM-related Metamemory Beliefs (PRMQ) with Cue Detection as a Moderator while controlling for only gender") %>%
  kable_styling(full_width = FALSE, position = "center") %>%
  add_header_above(c(" " = 1, "Standardized Beta" = 1, "Standard Error" = 1, "95% Confidence Interval" = 2, " " = 1)) %>%
  column_spec(2, bold = TRUE) %>%
  footnote(general = "Standardized Betas, standard errors, confidence intervals, and p-values for the indirect, direct, and total effects.",
           general_title = "Note: ")

# Create a new Word document
doc <- read_docx()

# Add the table to the Word document
doc <- doc %>%
  body_add_par("Model Results for CES-D Relating to PM Accuracy via PM-related Metamemory Beliefs (PRMQ) with Cue Detection as a Moderator while controlling for only gender", style = "heading 1") %>%
  body_add_table(value = results_table, style = "table_template") %>%  # You can define a style template in Word if you prefer
  body_add_par("Note: Standardized Betas, standard errors, confidence intervals, and p-values for the indirect, direct, and total effects.", style = "Normal")

# Save the document
print(doc, target = "CESD_gender_ModMediation_Analysis_Results.docx")

```


## PHQ9
### -1 SD
```{r}
model.M <- lm(PRMQ1 ~ PHQ9_c + Gender1, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + PHQ9_c * minus_N300_c + Gender1, data =PMD)
resultsP1 <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "PHQ9_c", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(resultsP1)
```
### Average
```{r}
model.M <- lm(PRMQ1 ~ PHQ9_c + Gender1, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + PHQ9_c * mean_N300_c + Gender1, data =PMD)
resultsP2 <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "PHQ9_c", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(resultsP2)
```
### +1 SD
```{r}
model.M <- lm(PRMQ1 ~ PHQ9_c + Gender1, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + PHQ9_c * plus_N300_c + Gender1, data =PMD)
resultsP3 <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "PHQ9_c", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(resultsP3)
```

## CESD
### -1 SD
```{r}
model.M <- lm(PRMQ1 ~ CESD_c + Gender1, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + CESD_c * minus_N300_c + Gender1, data =PMD)
resultsC1 <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "CESD_c", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(resultsC1)
```
### Average
```{r}
model.M <- lm(PRMQ1 ~ CESD_c + Gender1, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + CESD_c * mean_N300_c + Gender1, data =PMD)
resultsC2 <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "CESD_c", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(resultsC2)
```
### +1 SD
```{r}
model.M <- lm(PRMQ1 ~ CESD_c + Gender1, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + CESD_c * plus_N300_c + Gender1, data =PMD)
resultsC3 <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "CESD_c", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(resultsC3)
```

```{r}
# Load necessary libraries
library(officer)
library(kableExtra)

# Define lists of results
resultsC <- list(resultsC1, resultsC2, resultsC3)
resultsP <- list(resultsP1, resultsP2, resultsP3)

# Function to create tables and add them to a Word document
create_document <- function(results_list, doc_title, file_name) {
  # Create a new Word document
  doc <- read_docx()
  
  # Loop through each result in the list and add a table to the document
  for (i in seq_along(results_list)) {
    # Access the current result
    result <- results_list[[i]]
    
    # Extract effect estimates, confidence intervals, standard errors, and p-values
    indirect_effect <- result$d0
    indirect_ci <- c(result$d0.ci[1], result$d0.ci[2])
    indirect_se <- sd(result$d0.sims)
    indirect_p <- result$d0.p
    
    direct_effect <- result$z0
    direct_ci <- c(result$z0.ci[1], result$z0.ci[2])
    direct_se <- sd(result$z0.sims)
    direct_p <- result$z0.p
    
    total_effect <- result$tau.coef
    total_ci <- c(result$tau.ci[1], result$tau.ci[2])
    total_se <- sd(result$tau.sims)
    total_p <- result$tau.p
    
    # Create data frame with all values
    results_table <- data.frame(
      Effect = c("Indirect", "Direct", "Total"),
      Estimate = c(indirect_effect, direct_effect, total_effect),
      SE = c(indirect_se, direct_se, total_se),
      `CI Lower` = c(indirect_ci[1], direct_ci[1], total_ci[1]),
      `CI Upper` = c(indirect_ci[2], direct_ci[2], total_ci[2]),
      `p-value` = c(indirect_p, direct_p, total_p)
    )
    
    # Add title for each model's table in the Word document
    model_title <- paste0("Model Results - ", doc_title, " ", i)
    doc <- doc %>% 
      body_add_par(model_title, style = "heading 2") %>%
      body_add_table(value = results_table, style = "table_template") %>%
      body_add_par("Note: Standardized Betas, standard errors, confidence intervals, and p-values for the indirect, direct, and total effects.", style = "Normal")
  }
  
  # Save the document
  print(doc, target = file_name)
}

# Create the documents for both sets of results
create_document(resultsC, "CES-D Models (C1-C3)", "CESD_ModMediation_Results_C.docx")
create_document(resultsP, "PM Models (P1-P3)", "CESD_ModMediation_Results_P.docx")
```



```{r}
lm <- lm(Accuracy ~ PHQ9_c * PRMQ1_c + Gender1, PMD)
summary(lm)

lm <- lm(N300 ~ PHQ9_c * PRMQ1_c + Gender1, PMD)
summary(lm)

lm <- lm(Accuracy ~ N300_c * PRMQ1_c + Gender1, PMD)
summary(lm)
```

Interpretations: The interaction effect seems to be stronger for the CESD, although mediation still exists. 
Interaction is significant, mediation is marginal. When moderator is incorporated though, mediation
goes away. When examined at different levels, mediation is marginal at each level of moderation. 
Taken together, this suggests that the mediation effect is consistent and stable across
every level of the N300. The indirect effect may have gone away in the overall model because
it tested every level of the N300 and could have diluted the relationship at the different
levels of the N300. 

For PHQ9, the mediator may have a more robust role, but the moderator still provides valuable information. 
When incorporating the moderator, the mediation becomes marginally significant. When examined at different levels
of the moderator, each level is significant. This suggests that the moderator may contribute to the relationship,
but the mediator is more powerful and consistent in explaining the relationship between the PHQ9 and accuracy. 

# Run regression main effects with no covariates!

## PHQ9
```{r}
lm <- lm(scale(Accuracy) ~ scale(PHQ9), PMD)
summary(lm)

lm <- lm(scale(Accuracy) ~ scale(PRMQ1), PMD)
summary(lm)

lm <- lm(scale(PRMQ1) ~ scale(PHQ9), PMD)
summary(lm)
```

## CESD
```{r}
lm <- lm(scale(Accuracy) ~ scale(CESD), PMD)
summary(lm)

lm <- lm(scale(Accuracy) ~ scale(PRMQ1), PMD)
summary(lm)

lm <- lm(scale(PRMQ1) ~ scale(CESD), PMD)
summary(lm)

```

# Run interactions without controlling 
```{r}
lm <- lm(Accuracy ~ PHQ9_c * N300_c, PMD)
summary(lm)

lm <- lm(Accuracy ~ CESD_c * N300_c, PMD)
summary(lm)
```

## Simple slopes
### PHQ9
```{r}
fitInt <- lm(Accuracy ~ PHQ9_c * N300_c, data = PMD)
summary(fitInt)
library(interactions)
sim_slopes(
  fitInt,
  PHQ9_c,
  N300_c,
  mod2 = NULL,
  modx.values = NULL,
  mod2.values = NULL,
  centered = "none",
  data = PMD,
  cond.int = FALSE,
  johnson_neyman = TRUE,
  jnplot = FALSE,
  jnalpha = 0.05,
  robust = FALSE,
  digits = getOption("jtools-digits", default = 2),
  pvals = TRUE,
  confint = FALSE,
  ci.width = 0.95)
```
### CESD
```{r}
fitInt <- lm(Accuracy ~ CESD_c * N300_c, data = PMD)
summary(fitInt)

sim_slopes(
  fitInt,
  CESD_c,
  N300_c,
  mod2 = NULL,
  modx.values = NULL,
  mod2.values = NULL,
  centered = "none",
  data = PMD,
  cond.int = FALSE,
  johnson_neyman = TRUE,
  jnplot = FALSE,
  jnalpha = 0.05,
  robust = FALSE,
  digits = getOption("jtools-digits", default = 2),
  pvals = TRUE,
  confint = FALSE,
  ci.width = 0.95)
```

# Mediation with no covariates

## PHQ9
```{r}
model.M <- lm(PRMQ1 ~ PHQ9, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + PHQ9, data =PMD)
results_nomod <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "PHQ9", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(results_nomod)
```

## CESD
```{r}
model.M <- lm(PRMQ1 ~ CESD, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + CESD, data =PMD)
results_nomod <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "CESD", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(results_nomod)
```

# Moderated mediation without covariates
## PHQ9
```{r}
model.M <- lm(PRMQ1 ~ PHQ9_c, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + PHQ9_c * N300_c, data =PMD)
results <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "PHQ9_c", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(results)
```
## CESD
```{r}
model.M <- lm(PRMQ1 ~ CESD_c, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + CESD_c * N300_c, data =PMD)
results <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "CESD_c", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(results)
```

# Conditional indirect mediation effects not controlling for age
## Create different levels of moderator
```{r}
# Average N300 value
N300_c <- PMD$N300_c
mean_N300_c <- mean(PMD$N300_c)
PMD$mean_N300_c <- mean_N300_c

N300_c <- PMD$N300_c
sd_N300_c <- sd(PMD$N300_c)
PMD$sd_N300_c <- sd_N300_c

# +1 SD
sd_N300_c <- PMD$sd_N300_c
mean_N300_c <- mean_N300_c
plus_N300_c <- mean_N300_c + sd_N300_c
PMD$plus_N300_c <- plus_N300_c

# -1 SD
sd_N300_c <- PMD$sd_N300_c
mean_N300_c <- mean_N300_c
minus_N300_c <- mean_N300_c - sd_N300_c
PMD$minus_N300_c <- minus_N300_c
```

## PHQ9
### -1 SD
```{r}
model.M <- lm(PRMQ1 ~ PHQ9_c, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + PHQ9_c * minus_N300_c, data =PMD)
results <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "PHQ9_c", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(results)
```
### Average
```{r}
model.M <- lm(PRMQ1 ~ PHQ9_c, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + PHQ9_c * mean_N300_c, data =PMD)
results <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "PHQ9_c", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(results)
```
### +1 SD
```{r}
model.M <- lm(PRMQ1 ~ PHQ9_c, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + PHQ9_c * plus_N300_c, data =PMD)
results <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "PHQ9_c", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(results)
```

## CESD
### -1 SD
```{r}
model.M <- lm(PRMQ1 ~ CESD_c, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + CESD_c * minus_N300_c, data =PMD)
results <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "CESD_c", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(results)
```
### Average
```{r}
model.M <- lm(PRMQ1 ~ CESD_c, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + CESD_c * mean_N300_c, data =PMD)
results <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "CESD_c", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(results)
```
### +1 SD
```{r}
model.M <- lm(PRMQ1 ~ CESD_c, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + CESD_c * plus_N300_c, data =PMD)
results <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "CESD_c", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(results)
```

```{r}
lm <- lm(Accuracy ~ PHQ9_c * PRMQ1_c, PMD)
summary(lm)

lm <- lm(N300 ~ PHQ9_c * PRMQ1_c, PMD)
summary(lm)

lm <- lm(Accuracy ~ N300_c * PRMQ1_c, PMD)
summary(lm)
```
# Graphs!

##Graphs of main effects
## Make a scatterplot: Depression (PHQ9) & Accuracy
```{r}
p <- ggplot(PMD, aes(x = PHQ9, y = Accuracy)) +
  geom_point() +
    geom_smooth(method = "lm", se=FALSE, fullrange=TRUE, color = "black") + theme_minimal() + scale_color_grey()
p <- p + ggtitle("") + xlab("Depression (PHQ-9)") + ylab("PM Accuracy") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.text=element_text(size=18),
        axis.title=element_text(size=18,face="plain"))
p

ggsave("PHQ9_ACC", path = '/Users/mickey.rice/Desktop/', bg="white", width = 5, height = 5, device='jpeg', dpi= 700)
```

## Make a scatterplot: Depression (CESD) & Accuracy
```{r}
p <- ggplot(PMD, aes(x = CESD, y = Accuracy)) +
  geom_point() +
    geom_smooth(method = "lm", se=FALSE, fullrange=TRUE, color = "black") + theme_minimal() + scale_color_grey()
p <- p + ggtitle("") + xlab("Depression (CES-D)") + ylab("PM Accuracy") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.text=element_text(size=18),
        axis.title=element_text(size=18,face="plain"))
p

ggsave("CESD_ACC", path = '/Users/mickey.rice/Desktop/', bg="white", width = 5, height = 5, device='jpeg', dpi= 700)
```

## Interaction plots
```{r}
library(interactions)
library(ggplot2)

fitInt <- lm(Accuracy ~ PHQ9_c * N300_c + Gender1 + Age, data = PMD)

plot <- interact_plot(fitInt, pred = PHQ9_c, modx = N300_c, 
               plot.points = TRUE,    # To show individual data points
               interval = TRUE,       # To include confidence intervals
               colors = "Set1")       # Change colors if you prefer different ones


# Customize the axis titles
plot <- plot + 
  labs(x = "PHQ-9 Scores",  
       y = "Accuracy",
       color = "N300 Amplitudes") 

print(plot)

ggsave("PHQ9*N300_Accuracy", path = '/Users/mickey.rice/Desktop/', bg="white", width = 5, height = 5, device='jpeg', dpi= 700)
       
```

```{r}
library(interactions)
library(ggplot2)

fitInt <- lm(Accuracy ~ CESD_c * N300_c + Gender1 + Age, data = PMD)

plot <- interact_plot(fitInt, pred = CESD_c, modx = N300_c, 
               plot.points = TRUE,    # To show individual data points
               interval = TRUE,       # To include confidence intervals
               colors = "Set1")       # Change colors if you prefer different ones


# Customize the axis titles
plot <- plot + 
  labs(x = "CES-D Scores",  
       y = "Accuracy",
       color = "N300 Amplitudes") 

print(plot)

ggsave("CESD*N300_Accuracy", path = '/Users/mickey.rice/Desktop/', bg="white", width = 5, height = 5, device='jpeg', dpi= 700)
       
```
# Info for interaction tables 
## PHQ9
```{r}
# Control for age and gender
lm <- lm(scale(Accuracy) ~ scale(N300) + Gender1 + Age, PMD)
summary(lm)

lm <- lm(scale(Accuracy) ~ scale(PHQ9) + Gender1 + Age, PMD)
summary(lm)

lm <- lm(Accuracy ~ PHQ9_c * N300_c + Gender1 + Age, PMD)
summary(lm)


# Only control for gender
lm <- lm(scale(Accuracy) ~ scale(N300) + Gender1, PMD)
summary(lm)

lm <- lm(scale(Accuracy) ~ scale(PHQ9) + Gender1, PMD)
summary(lm)

lm <- lm(Accuracy ~ PHQ9_c * N300_c + Gender1, PMD)
summary(lm)

```


## CESD
```{r}
# Control for age and gender
lm <- lm(scale(Accuracy) ~ scale(N300) + Gender1 + Age, PMD)
summary(lm)

lm <- lm(scale(Accuracy) ~ scale(CESD) + Gender1 + Age, PMD)
summary(lm)

lm <- lm(Accuracy ~ CESD_c * N300_c + Gender1 + Age, PMD)
summary(lm)


# Only control for gender
lm <- lm(scale(Accuracy) ~ scale(N300) + Gender1, PMD)
summary(lm)

lm <- lm(scale(Accuracy) ~ scale(CESD) + Gender1, PMD)
summary(lm)

lm <- lm(Accuracy ~ CESD_c * N300_c + Gender1, PMD)
summary(lm)

```

# Info for main effect tables 
##PHQ9
```{r}
# Control for age and gender
lm <- lm(scale(Accuracy) ~ scale(PRMQ1) + Gender1 + Age, PMD)
summary(lm)

lm <- lm(scale(Accuracy) ~ scale(PHQ9) + Gender1 + Age, PMD)
summary(lm)

lm <- lm(scale(PRMQ1) ~ scale(PHQ9) + Gender1 + Age, PMD)
summary(lm)

# Only control for gender
lm <- lm(scale(Accuracy) ~ scale(PRMQ1) + Gender1, PMD)
summary(lm)

lm <- lm(scale(Accuracy) ~ scale(PHQ9) + Gender1, PMD)
summary(lm)

lm <- lm(scale(PRMQ1) ~ scale(PHQ9) + Gender1, PMD)
summary(lm)

```
## CESD
```{r}
# Control for age and gender
lm <- lm(scale(Accuracy) ~ scale(PRMQ1) + Gender1 + Age, PMD)
summary(lm)

lm <- lm(scale(Accuracy) ~ scale(CESD) + Gender1 + Age, PMD)
summary(lm)

lm <- lm(scale(PRMQ1) ~ scale(CESD) + Gender1 + Age, PMD)
summary(lm)

# Only control for gender
lm <- lm(scale(Accuracy) ~ scale(PRMQ1) + Gender1, PMD)
summary(lm)

lm <- lm(scale(Accuracy) ~ scale(CESD) + Gender1, PMD)
summary(lm)

lm <- lm(scale(PRMQ1) ~ scale(CESD) + Gender1, PMD)
summary(lm)
```

