---
title: "Paper 2"
output: 
  html_notebook:
    toc: yes
  html_document:
    toc: yes
    df_print: paged
---

Created by Mickey Rice
October 10th, 2024

# Load Libaries 
```{r}
library(psych)
library(dplyr)
library(tidyverse)
library(apaTables)
library(ggplot2)

```

# Load Data 
```{r}
PMD <- read_csv("PMD.csv")
```

# Recode variables 
```{r}

PMD$Sex1<- 0
PMD$Sex1<-ifelse(PMD$Gender=="Male",-1, 1)


PMD$Gender1<- 0
PMD$Gender1<-ifelse(PMD$Gender=="Male", 0, 
                    ifelse(PMD$Gender=="Female", 1, 2))

## Explaining code : PM$Gender1<- 0 creates the new variable titled Gender1 
## PM$Gender1<-ifelse(PM$Gender ==“Male”,0 , ifelse(PM$Gender=="Female", 1, 2))) says “if the Gender is male, they will be 0, if Gender is female, they will be 1, if Gender is anything else it will be 2" 

```


```{r}
print(PMD)

describe(PMD)
```

# Print correlation tables
```{r}
library(apaTables)

# for Paper 2

#zero order correlation table 
desctable2 <- select(PMD, PP, N300, PRMQ1, Confidence, JOL, PHQ9, CESD, Age, Gender1)

apa.cor.table(
      desctable2,
      filename = "desctablePaper2.doc",
      table.number = 1,
      show.conf.interval = TRUE,
      show.sig.stars = TRUE,
      landscape = TRUE
)

#zero order correlation table 
desctable2 <- select(PMD, PP, N300, PRMQ1, Confidence, JOL, Motivation, ADHD, HrsSleep, Sleepiness, PosAff, NegAff, STAIS)

apa.cor.table(
      desctable2,
      filename = "desctable2Paper2.doc",
      table.number = 1,
      show.conf.interval = TRUE,
      show.sig.stars = TRUE,
      landscape = TRUE
)
```

# Correlations: Gender and age with variables
```{r}
gender <- lm(PHQ9 ~ Gender1, data = PMD)
summary(gender)

gender <- lm(CESD ~ Gender1, data = PMD)
summary(gender)

gender <- lm(PRMQ1 ~ Gender1, data = PMD)
summary(gender)

```

## GenderMW
```{r}
# Gender

# Recode for point biserial correlations
PMD$GenderNew<- 0

PMD$GenderNew<-ifelse(PMD$Gender=="Male", "Man", 
                    ifelse(PMD$Gender=="Female", "Woman", "Trans"))

# df1: Man = 0, Woman = 1. 
df1 <- PMD[PMD$GenderNew %in% c("Man", "Woman"), ]
df1$GenderMW <- ifelse(df1$GenderNew == "Man", 0, 1)


# Loop through all the correlations!
dependent_vars <- c("PP", "N300", "PRMQ1", "Confidence", "JOL", "PHQ9", "CESD", "Age")

# Initialize a list to store results
results <- list()

# Loop through each dependent variable
for (var in dependent_vars) {
    # Perform the correlation test
    correlation_result <- cor.test(df1$GenderMW, df1[[var]], method = "pearson")
    
    # Store the results in the list
    results[[var]] <- correlation_result
}

# Print the results
for (var in dependent_vars) {
    print(paste("Correlation results for:", var))
    print(results[[var]])
}

```
## GenderWT
```{r}
# Recode for point biserial correlations
# df2: Women = 0, Transgender + nonbinary = 1. 
df2 <- PMD[PMD$GenderNew %in% c("Woman", "Trans"), ]
df2$GenderWT <- ifelse(df2$GenderNew == "Woman", 0, 1)


# Loop through all the correlations!
dependent_vars <- c("PP", "N300", "PRMQ1", "Confidence", "JOL", "PHQ9", "CESD", "Age")

# Initialize a list to store results
results <- list()

# Loop through each dependent variable
for (var in dependent_vars) {
    # Perform the correlation test
    correlation_result <- cor.test(df2$GenderWT, df2[[var]], method = "pearson")
    
    # Store the results in the list
    results[[var]] <- correlation_result
}

# Print the results
for (var in dependent_vars) {
    print(paste("Correlation results for:", var))
    print(results[[var]])
}
```

## GenderMT
```{r}
# Recode for point biserial correlations
# df3: Men = 0, Transgender + nonbinary = 1.
df3 <- PMD[PMD$GenderNew %in% c("Man", "Trans"), ]
df3$GenderMT <- ifelse(df3$GenderNew == "Man", 0, 1)


# Loop through all the correlations!
dependent_vars <- c("PP", "N300", "PRMQ1", "Confidence", "JOL", "PHQ9", "CESD", "Age")

# Initialize a list to store results
results <- list()

# Loop through each dependent variable
for (var in dependent_vars) {
    # Perform the correlation test
    correlation_result <- cor.test(df3$GenderMT, df3[[var]], method = "pearson")
    
    # Store the results in the list
    results[[var]] <- correlation_result
}

# Print the results
for (var in dependent_vars) {
    print(paste("Correlation results for:", var))
    print(results[[var]])
}

```

# Sample info

```{r}
PMD %>%
  count(Gender)

PMD %>%
  count(Race)

PMD %>%
  count(Ethnicity)

PMD %>%
  count(Handedness)

describe(PMD$PHQ9)

describe(PMD$CESD)

describe(PMD$JOL)

describe(PMD$Accuracy)

describe(PMD$RT)
2093.87 - 282.68

describe(PMD$Motivation)
204 - 84

describe(PMD$ADHD)

describe(PMD$HrsSleep)

describe(PMD$Sleepiness)

PMD %>% count(PHQ9 <= 3)

PMD %>% count(PHQ9 >= 15 & PHQ9 <= 19)

PMD %>% count(PHQ9 >= 20)

PMD %>% count(CESD <= 16)

73/80

```


# Regression Main effects-------------------------------------------------------

## Regression: Depression predicting Metamemory controlling for age and gender 
```{r}
## scale = standardizing the coefficients 

fit4 <- lm(scale(PRMQ1) ~ scale(PHQ9) + Gender1 + Age, data = PMD)
summary(fit4)

fit5 <- lm(scale(Confidence) ~ scale(PHQ9) + Gender1 + Age, data = PMD)
summary(fit5)

fit6 <- lm(scale(JOL) ~ scale(PHQ9) + Gender1 + Age, data = PMD)
summary(fit6)

fit7 <- lm(scale(PRMQ1) ~ scale(CESD) + Gender1 + Age, data = PMD)
summary(fit7)

fit8 <- lm(scale(Confidence) ~ scale(CESD) + Gender1 + Age, data = PMD)
summary(fit8)

fit9 <- lm(scale(JOL) ~ scale(CESD) + Gender1 + Age, data = PMD)
summary(fit9)

# fit10 <- lm(scale(PRMQ1) ~ scale(DASS) + Gender1 + Age, data = PMD)
# summary(fit10)

# fit11 <- lm(scale(Confidence) ~ scale(DASS) + Gender1 + Age, data = PMD)
# summary(fit11)

# fit12 <- lm(scale(JOL) ~ scale(DASS) + Gender1 + Age, data = PMD)
# summary(fit12)
```

## Regression: Depression predicting Metamemory not controlling
```{r}
## scale = standardizing the coefficients 

fit4 <- lm(scale(PRMQ1) ~ scale(PHQ9), data = PMD)
summary(fit4)

fit5 <- lm(scale(Confidence) ~ scale(PHQ9), data = PMD)
summary(fit5)

fit6 <- lm(scale(JOL) ~ scale(PHQ9), data = PMD)
summary(fit6)

fit7 <- lm(scale(PRMQ1) ~ scale(CESD), data = PMD)
summary(fit7)

fit8 <- lm(scale(Confidence) ~ scale(CESD), data = PMD)
summary(fit8)

fit9 <- lm(scale(JOL) ~ scale(CESD), data = PMD)
summary(fit9)
```

## Regression: Depression predicting N300 not controlling
```{r}
## scale = standardizing the coefficients 

fit4 <- lm(scale(N300) ~ scale(PHQ9), data = PMD)
summary(fit4)

fit7 <- lm(scale(N300) ~ scale(CESD), data = PMD)
summary(fit7)

# fit10 <- lm(scale(N300) ~ scale(DASS) + Gender1 + Age, data = PMD)
# summary(fit10)

```

## Regression: Depression predicting PP not controlling
```{r}
## scale = standardizing the coefficients 

fit4 <- lm(scale(PP) ~ scale(PHQ9), data = PMD)
summary(fit4)

fit7 <- lm(scale(PP) ~ scale(CESD), data = PMD)
summary(fit7)

# fit10 <- lm(scale(N300) ~ scale(DASS) + Gender1 + Age, data = PMD)
# summary(fit10)

```


## Regression: Depression predicting PP controlling for age and gender
```{r}
## scale = standardizing the coefficients 

fit4 <- lm(scale(PP) ~ scale(PHQ9) + Gender1 + Age, data = PMD)
summary(fit4)

fit7 <- lm(scale(PP) ~ scale(CESD) + Gender1 + Age, data = PMD)
summary(fit7)

# fit10 <- lm(scale(PP) ~ scale(DASS) + Gender1 + Age, data = PMD)
# summary(fit10)

```

# Interaction effects-----------------------------------------------------------

## Centering the variables for an interaction
```{r}
## centering the variable - most important for interaction
PHQ9 <- PMD$PHQ9
mean_PHQ9 <- mean(PHQ9)
PHQ9_c <- PHQ9 - mean_PHQ9
PMD$PHQ9_c <- PHQ9_c

CESD <- PMD$CESD
mean_CESD <- mean(CESD)
CESD_c <- CESD - mean_CESD
PMD$CESD_c <- CESD_c

DASS <- PMD$DASS
mean_DASS <- mean(DASS)
DASS_c <- DASS - mean_DASS
PMD$DASS_c <- DASS_c

PRMQ1 <- PMD$PRMQ1
mean_PRMQ1 <- mean(PRMQ1)
PRMQ1_c <- PRMQ1 - mean_PRMQ1
PMD$PRMQ1_c <- PRMQ1_c

Confidence <- PMD$Confidence
mean_Confidence <- mean(Confidence)
Confidence_c <- Confidence - mean_Confidence
PMD$Confidence_c <- Confidence_c

N300 <- PMD$N300
mean_N300 <- mean(N300)
N300_c <- N300 - mean_N300
PMD$N300_c <- N300_c

PP <- PMD$PP
mean_PP <- mean(PP)
PP_c <- PP - mean_PP
PMD$PP_c <- PP_c

JOL <- PMD$JOL
mean_JOL <- mean(JOL)
JOL_c <- JOL - mean_JOL
PMD$JOL_c <- JOL_c

# PM$Gender1_f <- as.factor(PM$Gender1)

# contrasts(PM$Gender1_f) <- contr.helmert(n = 3)

```

# Interaction: Depression and Metamemory on ERPs
## PRMQ1
```{r}
## PP
fit <- lm(PP ~ PHQ9_c * PRMQ1_c + Gender1 + Age, data = PMD)
summary(fit)

fit <- lm(PP ~ CESD_c * PRMQ1_c + Gender1 + Age, data = PMD)
summary(fit)

# N300
fit <- lm(N300 ~ PHQ9_c * PRMQ1_c + Gender1 + Age, data = PMD)
summary(fit)

fit <- lm(N300 ~ CESD_c * PRMQ1_c + Gender1 + Age, data = PMD)
summary(fit)


# fit <- lm(PP ~ DASS_c * PRMQ1_c + DASS_c + PRMQ1_c, data = PMD)
# summary(fit)

# fit <- lm(N300 ~ DASS_c * PRMQ1_c + DASS_c + PRMQ1_c, data = PMD)
# summary(fit)

```
# Interaction: Depression and Metamemory on ERPs not controlling
## PRMQ1
```{r}
## PP
fit <- lm(PP ~ PHQ9_c * PRMQ1_c, data = PMD)
summary(fit)

fit <- lm(PP ~ CESD_c * PRMQ1_c, data = PMD)
summary(fit)

# N300
fit <- lm(N300 ~ PHQ9_c * PRMQ1_c, data = PMD)
summary(fit)

fit <- lm(N300 ~ CESD_c * PRMQ1_c, data = PMD)
summary(fit)

# fit <- lm(PP ~ DASS_c * PRMQ1_c + DASS_c + PRMQ1_c, data = PMD)
# summary(fit)

# fit <- lm(N300 ~ DASS_c * PRMQ1_c + DASS_c + PRMQ1_c, data = PMD)
# summary(fit)
```



## Confidence
```{r}
# PP
fit <- lm(PP ~ PHQ9_c * Confidence_c + Gender1 + Age, data = PMD)
summary(fit)

fit <- lm(PP ~ CESD_c * Confidence_c + Gender1 + Age, data = PMD)
summary(fit)

# N300
fit <- lm(N300 ~ PHQ9_c * Confidence_c + Gender1 + Age, data = PMD)
summary(fit)

fit <- lm(N300 ~ CESD_c * Confidence_c + Gender1 + Age, data = PMD)
summary(fit)
```

## Confidence 
```{r}
# PP
fit <- lm(PP ~ PHQ9_c * Confidence_c, data = PMD)
summary(fit)

fit <- lm(PP ~ CESD_c * Confidence_c, data = PMD)
summary(fit)

# N300
fit <- lm(N300 ~ PHQ9_c * Confidence_c, data = PMD)
summary(fit)

fit <- lm(N300 ~ CESD_c * Confidence_c, data = PMD)
summary(fit)
```


## JOL
```{r}
# PP
fit <- lm(PP ~ PHQ9_c * JOL_c, data = PMD)
summary(fit)

fit <- lm(PP ~ CESD_c * JOL_c, data = PMD)
summary(fit)

# N300
fit <- lm(N300 ~ PHQ9_c * JOL_c, data = PMD)
summary(fit)

fit <- lm(N300 ~ CESD_c * JOL_c, data = PMD)
summary(fit)
```
## JOL
```{r}
# PP
fit <- lm(PP ~ PHQ9_c * JOL_c + Gender1 + Age, data = PMD)
summary(fit)

fit <- lm(PP ~ CESD_c * JOL_c + Gender1 + Age, data = PMD)
summary(fit)

# N300
fit <- lm(N300 ~ PHQ9_c * JOL_c + Gender1 + Age, data = PMD)
summary(fit)

fit <- lm(N300 ~ CESD_c * JOL_c + Gender1 + Age, data = PMD)
summary(fit)
```


## Simple slopes

### Interaction of PRMQ and PHQ9 on N300
```{r}
library(jtools)
library(rlang)
library(interactions)

fitInt <- lm(N300 ~ PHQ9_c * PRMQ1_c + Gender1 + Age, data = PMD)
summary(fitInt)

sim_slopes(
  fitInt,
  PHQ9_c,
  PRMQ1_c,
  mod2 = NULL,
  modx.values = NULL,
  mod2.values = NULL,
  centered = "none",
  data = PMD,
  cond.int = FALSE,
  johnson_neyman = TRUE,
  jnplot = FALSE,
  jnalpha = 0.05,
  robust = FALSE,
  digits = getOption("jtools-digits", default = 2),
  pvals = TRUE,
  confint = FALSE,
  ci.width = 0.95)
```

## Graph
```{r}
library(interactions)
library(ggplot2)

fitInt <- lm(N300 ~ PHQ9_c * PRMQ1_c + Gender1 + Age, data = PMD)

plot <- interact_plot(fitInt, pred = PHQ9_c, modx = PRMQ1_c, 
               plot.points = TRUE,    # To show individual data points
               interval = FALSE,       # To include confidence intervals
               colors = "Set1")       # Change colors if you prefer different ones

# Customize the axis titles
plot <- plot + 
  labs(x = "PHQ-9 Scores",  
       y = "N300 Amplitude (µV)",
       color = "PRMQ1 Scores") 

print(plot)

ggsave("PRMQ*PHQ9_N300", path = '/Users/mickey.rice/Desktop/', bg="white", width = 5, height = 5, device='jpeg', dpi= 700)
       
```


### Interaction of JOL and PHQ9 on N300
```{r}
library(jtools)
library(rlang)
library(interactions)

fitInt <- lm(N300 ~ PHQ9_c * JOL_c + Gender1 + Age, data = PMD)
summary(fitInt)

sim_slopes(
  fitInt,
  PHQ9_c,
  JOL_c,
  mod2 = NULL,
  modx.values = NULL,
  mod2.values = NULL,
  centered = "none",
  data = PMD,
  cond.int = FALSE,
  johnson_neyman = TRUE,
  jnplot = FALSE,
  jnalpha = 0.05,
  robust = FALSE,
  digits = getOption("jtools-digits", default = 2),
  pvals = TRUE,
  confint = FALSE,
  ci.width = 0.95)
```

## Graph
```{r}
library(interactions)
library(ggplot2)

fitInt <- lm(N300 ~ PHQ9_c * JOL_c + Gender1 + Age, data = PMD)

plot <- interact_plot(fitInt, pred = PHQ9_c, modx = JOL_c, 
               plot.points = TRUE,    # To show individual data points
               interval = TRUE,       # To include confidence intervals
               colors = "Set1")       # Change colors if you prefer different ones


# Customize the axis titles
plot <- plot + 
  labs(x = "PHQ-9 Scores",  
       y = "N300 Amplitude (µV)",
       color = "Performance Prediction") 

print(plot)

ggsave("JOL*PHQ9_N300", path = '/Users/mickey.rice/Desktop/', bg="white", width = 5, height = 5, device='jpeg', dpi= 700)
       
```


# Effect sizes------------------------------------------------------------------

## Partial R-squared for PHQ9 on PRMQ1
```{r}
#full linear regression model
full_model <- lm(PRMQ1 ~ PHQ9 + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(PRMQ1 ~ Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## Partial R-squared for PHQ9 on Confidence
```{r}
#full linear regression model
full_model <- lm(Confidence ~ PHQ9 + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(Confidence ~ Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## Partial R-squared for PHQ9 on JOL
```{r}
#full linear regression model
full_model <- lm(JOL ~ PHQ9 + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(JOL ~ Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## Partial R-squared for CESD on PRMQ1
```{r}
#full linear regression model
full_model <- lm(PRMQ1 ~ CESD + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(PRMQ1 ~ Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## Partial R-squared for CESD on Confidence
```{r}
#full linear regression model
full_model <- lm(Confidence ~ CESD + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(Confidence ~ Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```


## Partial R-squared for CESD on JOL
```{r}
#full linear regression model
full_model <- lm(JOL ~ CESD + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(JOL ~ Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```


## Partial R-squared for PHQ9 on PP
```{r}
#full linear regression model
full_model <- lm(PP ~ PHQ9 + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(PP ~ Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## Partial R-squared for PHQ9 on N300
```{r}
#full linear regression model
full_model <- lm(N300 ~ PHQ9 + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(N300 ~ Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## Partial R-squared for CESD on PP
```{r}
#full linear regression model
full_model <- lm(PP ~ CESD + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(PP ~ Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```


## Partial R-squared for CESD on N300
```{r}
#full linear regression model
full_model <- lm(N300 ~ CESD + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(N300 ~ Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## Partial R-squared for CESD_c*JOL on PP
```{r}
#full linear regression model
full_model <- lm(PP ~ CESD_c*JOL_c + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(PP ~ CESD_c + JOL_c + Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## Interactions: PP
## Partial R-squared for PHQ9*PRMQ1 on PP
```{r}
#full linear regression model
full_model <- lm(PP ~ PHQ9_c*PRMQ1_c + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(PP ~ PHQ9_c + PRMQ1_c + Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## Partial R-squared for PHQ9*Confidence on PP
```{r}
#full linear regression model
full_model <- lm(PP ~ PHQ9_c*Confidence_c + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(PP ~ PHQ9_c + Confidence_c + Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## Partial R-squared for PHQ9*JOL on PP
```{r}
#full linear regression model
full_model <- lm(PP ~ PHQ9_c*JOL_c + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(PP ~ PHQ9_c + JOL_c + Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## Partial R-squared for CESD*PRMQ1 on PP
```{r}
#full linear regression model
full_model <- lm(PP ~ CESD_c*PRMQ1_c + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(PP ~ CESD_c + PRMQ1_c + Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## Partial R-squared for CESD_c*Confidence on PP
```{r}
#full linear regression model
full_model <- lm(PP ~ CESD_c*Confidence_c + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(PP ~ CESD_c + Confidence_c + Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## Partial R-squared for CESD_c*JOL on PP
```{r}
#full linear regression model
full_model <- lm(PP ~ CESD_c*JOL_c + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(PP ~ CESD_c + JOL_c + Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## Interaction: N300
## Partial R-squared for PHQ9*PRMQ1 on N300
```{r}
#full linear regression model
full_model <- lm(N300 ~ PHQ9_c*PRMQ1_c + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(N300 ~ PHQ9_c + PRMQ1_c + Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## Partial R-squared for PHQ9*Confidence on N300
```{r}
#full linear regression model
full_model <- lm(N300 ~ PHQ9_c*Confidence_c + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(N300 ~ PHQ9_c + Confidence_c + Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## Partial R-squared for PHQ9*JOL on N300
```{r}
#full linear regression model
full_model <- lm(N300 ~ PHQ9_c*JOL_c + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(N300 ~ PHQ9_c + JOL_c + Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## Partial R-squared for CESD*PRMQ1 on N300
```{r}
#full linear regression model
full_model <- lm(N300 ~ CESD_c*PRMQ1_c + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(N300 ~ CESD_c + PRMQ1_c + Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```


## Partial R-squared for CESD*Confidence on N300
```{r}
#full linear regression model
full_model <- lm(N300 ~ CESD_c*Confidence_c + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(N300 ~ CESD_c + Confidence_c + Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## Partial R-squared for CESD_c*JOL on N300
```{r}
#full linear regression model
full_model <- lm(N300 ~ CESD_c*JOL_c + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(N300 ~ CESD_c + JOL_c + Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

# Graphs of main effects
## Make a scatterplot: Depression (PHQ9) & PRMQ
```{r}
p <- ggplot(PMD, aes(x = PHQ9, y = PRMQ1)) +
  geom_point() +
    geom_smooth(method = "lm", se=FALSE, fullrange=TRUE, color = "black") + theme_minimal() + scale_color_grey()
p <- p + ggtitle("") + xlab("Depression (PHQ-9)") + ylab("Poor PM Beliefs") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.text=element_text(size=18),
        axis.title=element_text(size=18,face="plain"))
p

ggsave("PHQ9_PRMQ", path = '/Users/mickey.rice/Desktop/', bg="white", width = 5, height = 5, device='jpeg', dpi= 700)
```

## Make a scatterplot: Depression (PHQ9) & Confidence
```{r}
p <- ggplot(PMD, aes(x = PHQ9, y = Confidence)) +
  geom_point() +
    geom_smooth(method = "lm", se=FALSE, fullrange=TRUE, color = "black") + theme_minimal() + scale_color_grey()
p <- p + ggtitle("") + xlab("Depression (PHQ-9)") + ylab("Poor Cognitive Confidence") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.text=element_text(size=18),
        axis.title=element_text(size=18,face="plain"))
p

ggsave("PHQ9_Confidence", path = '/Users/mickey.rice/Desktop/', bg="white", width = 5, height = 5, device='jpeg', dpi= 700)
```

## Make a scatterplot: Depression (CESD) & PRMQ
```{r}
p <- ggplot(PMD, aes(x = CESD, y = PRMQ1)) +
  geom_point() +
    geom_smooth(method = "lm", se=FALSE, fullrange=TRUE, color = "black") + theme_minimal() + scale_color_grey()
p <- p + ggtitle("") + xlab("Depression (CES-D)") + ylab("Poor PM Beliefs") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.text=element_text(size=18),
        axis.title=element_text(size=18,face="plain"))
p

ggsave("CESD_PRMQ", path = '/Users/mickey.rice/Desktop/', bg="white", width = 5, height = 5, device='jpeg', dpi= 700)
```

## Make a scatterplot: Depression (PHQ9) & Confidence
```{r}
p <- ggplot(PMD, aes(x = CESD, y = Confidence)) +
  geom_point() +
    geom_smooth(method = "lm", se=FALSE, fullrange=TRUE, color = "black") + theme_minimal() + scale_color_grey()
p <- p + ggtitle("") + xlab("Depression (CES-D)") + ylab("Poor Cognitive Confidence") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.text=element_text(size=18),
        axis.title=element_text(size=18,face="plain"))
p

ggsave("CESD_Confidence", path = '/Users/mickey.rice/Desktop/', bg="white", width = 5, height = 5, device='jpeg', dpi= 700)
```

# Extra graph info 

```{r}
## A more complicated graph 
# Create a new dataset for predictions
pred_data <- expand.grid(
  PHQ9_c = seq(min(PMD$PHQ9_c), max(PMD$PHQ9_c), length.out = 100), # Range of PHQ9_c
  PRMQ1_c = c(mean(PMD$PRMQ1_c) - sd(PMD$PRMQ1_c),  # One standard deviation below the mean
              mean(PMD$PRMQ1_c),                    # Mean
              mean(PMD$PRMQ1_c) + sd(PMD$PRMQ1_c))  # One standard deviation above the mean
)

# Predict N300 for the new dataset using the model
pred_data$N300_pred <- predict(lm(N300 ~ PHQ9_c * PRMQ1_c + PHQ9_c + PRMQ1_c, data = PMD), newdata = pred_data)

# Convert PRMQ1_c to a factor for plotting
pred_data$PRMQ1_c <- factor(pred_data$PRMQ1_c, labels = c("Low PRMQ1", "Mean PRMQ1", "High PRMQ1"))

# Create the plot
ggplot(pred_data, aes(x = PHQ9_c, y = N300_pred, color = PRMQ1_c)) +
  geom_line(size = 1.2) +
  labs(title = "Interaction Effect of PHQ9_c and PRMQ1_c on N300",
       x = "PHQ9_c (Depression Score)",
       y = "Predicted N300",
       color = "PRMQ1_c") +
  theme_minimal() +
  theme(legend.position = "top") +
  scale_color_manual(values = c("blue", "orange", "green"))  # Customize colors if desired

```

# Exploratory Interaction: Depression and ERPs on metamemory---------------------

## PRMQ1
```{r}
fit <- lm(PRMQ1 ~ PHQ9_c * N300_c + Gender1 + Age, data = PMD)
summary(fit)

fit <- lm(PRMQ1 ~ PHQ9_c * PP_c + Gender1 + Age, data = PMD)
summary(fit)

fit <- lm(PRMQ1 ~ CESD_c * N300_c + Gender1 + Age, data = PMD)
summary(fit)

fit <- lm(PRMQ1 ~ CESD_c * PP_c + Gender1 + Age, data = PMD)
summary(fit)

```

## Confidence
```{r}
fit <- lm(Confidence ~ PHQ9_c * N300_c + Gender1 + Age, data = PMD)
summary(fit)

fit <- lm(Confidence ~ PHQ9_c * PP_c + Gender1 + Age, data = PMD)
summary(fit)

fit <- lm(Confidence ~ CESD_c * N300_c + Gender1 + Age, data = PMD)
summary(fit)

fit <- lm(Confidence ~ CESD_c * PP_c + Gender1 + Age, data = PMD)
summary(fit)

```

## JOL
```{r}
fit <- lm(JOL ~ PHQ9_c * N300_c + Gender1 + Age, data = PMD)
summary(fit)

fit <- lm(JOL ~ PHQ9_c * PP_c + Gender1 + Age, data = PMD)
summary(fit)

fit <- lm(JOL ~ CESD_c * N300_c + Gender1 + Age, data = PMD)
summary(fit)

fit <- lm(JOL ~ CESD_c * PP_c + Gender1 + Age, data = PMD)
summary(fit)

```

### Interaction of N300 and PHQ9 on PRMQ
```{r}
library(jtools)
library(rlang)

fitInt <- lm(PRMQ1 ~ PHQ9_c * N300_c + Gender1 + Age, data = PMD)
summary(fitInt)

sim_slopes(
  fitInt,
  PHQ9_c,
  N300_c,
  mod2 = NULL,
  modx.values = NULL,
  mod2.values = NULL,
  centered = "none",
  data = PMD,
  cond.int = FALSE,
  johnson_neyman = TRUE,
  jnplot = FALSE,
  jnalpha = 0.05,
  robust = FALSE,
  digits = getOption("jtools-digits", default = 2),
  pvals = TRUE,
  confint = FALSE,
  ci.width = 0.95)
```

```{r}
library(interactions)
library(ggplot2)

fitInt <- lm(PRMQ1 ~ PHQ9_c * N300_c + Gender1 + Age, data = PMD)

interact_plot(fitInt, pred = PHQ9_c, modx = N300_c, 
               plot.points = TRUE,    # To show individual data points
               interval = TRUE,       # To include confidence intervals
               colors = "Set1")       # Change colors if you prefer different ones
```

### Interaction of N300 and PHQ9 on JOL
```{r}
library(jtools)
library(rlang)

fitInt <- lm(JOL ~ PHQ9_c * N300_c + Gender1 + Age, data = PMD)
summary(fitInt)

sim_slopes(
  fitInt,
  PHQ9_c,
  N300_c,
  mod2 = NULL,
  modx.values = NULL,
  mod2.values = NULL,
  centered = "none",
  data = PMD,
  cond.int = FALSE,
  johnson_neyman = TRUE,
  jnplot = FALSE,
  jnalpha = 0.05,
  robust = FALSE,
  digits = getOption("jtools-digits", default = 2),
  pvals = TRUE,
  confint = FALSE,
  ci.width = 0.95)
```

```{r}
library(interactions)
library(ggplot2)

fitInt <- lm(JOL ~ PHQ9_c * N300_c + Gender1 + Age, data = PMD)

interact_plot(fitInt, pred = PHQ9_c, modx = N300_c, 
               plot.points = TRUE,    # To show individual data points
               interval = TRUE,       # To include confidence intervals
               colors = "Set1")       # Change colors if you prefer different ones
```


# Sensitivity analyses----------------------------------------------------------

## SES

# Averaging SES
```{r}
PMD$pared1 <- as.numeric(as.character(PMD$pared1))
PMD$pared2 <- as.numeric(as.character(PMD$pared2))

PMD <- PMD %>%
  mutate(avgpared = rowMeans(select(., pared1, pared2), na.rm = TRUE))

# View the updated dataframe
print(PMD)

describe(PMD)

```

## Extra variables in the regression models
```{r}
library(openxlsx)

# List of dependent variables
dependent_vars <- c('PRMQ1', 'Confidence', 'JOL', 'PP', 'N300')

# Independent variables to be tested sequentially
selected_columns <- c('PHQ9', 'CESD')

# List of additional controls
additional_controls <- list(
  SES = "PMD$avgpared",       # Socioeconomic status
  ADHD = "PMD$ADHD",     # ADHD symptoms
  Motivation = "PMD$Motivation", # motivation score
  Sleepiness = "PMD$Sleepiness", # Sleepiness score
  HrsSleep = "PMD$HrsSleep", # Hours of sleep the night before
  Anxiety = 'STAIS', # state anxiety
  PositiveAff = 'PosAff', # positive affect
  NegativeAff = 'NegAff' # negative affect
)

# Initialize the results dataframe
results <- data.frame(Dependent_Variable = character(), 
                      Independent_Variable = character(), 
                      Control_Variable = character(),
                      Estimate = numeric(), 
                      P_Value = numeric(), 
                      stringsAsFactors = FALSE)

# Outer loop for dependent variables
for (dep_var in dependent_vars) {
  
  # Inner loop for independent variables (tested sequentially)
  for (col in selected_columns) {
    
    # Loop for additional controls
    for (control_name in names(additional_controls)) {
      control_var <- additional_controls[[control_name]]
      
      # Construct the formula for each model
      formula_str <- paste("PMD$", dep_var, " ~ PMD$", col, " + PMD$Gender1 + PMD$Age + ", control_var, sep = "")
      
      # Run the linear model
      lm1 <- lm(as.formula(formula_str), data = PMD)
      summary_lm1 <- summary(lm1)
      
      # Extract estimate and p-value for the variable of interest (col)
      estimate <- summary_lm1$coefficients[2, 1]  # 2nd row, 1st column (estimate)
      p_value <- summary_lm1$coefficients[2, 4]   # 2nd row, 4th column (p-value)
      
      # Store the result in the results dataframe
      results <- rbind(results, data.frame(Dependent_Variable = dep_var, 
                                           Independent_Variable = col, 
                                           Control_Variable = control_name,
                                           Estimate = estimate, 
                                           P_Value = p_value))
    }
  }
}

# Write the results to an Excel file
write.xlsx(results, file = "/Users/mickey.rice/Desktop/results2.xlsx", rowNames = FALSE)
```


## Extra variables in the interaction models
```{r}
library(openxlsx)

# List of dependent variables
dependent_vars <- c('PP', 'N300')

# List of additional controls
additional_controls <- list(
  SES = "PMD$avgpared",       # Socioeconomic status
  ADHD = "PMD$ADHD",     # ADHD symptoms
  Motivation = "PMD$Motivation", # motivation score
  Sleepiness = "PMD$Sleepiness", # Sleepiness score
  HrsSleep = "PMD$HrsSleep", # Hours of sleep the night before
  Anxiety = 'STAIS', # state anxiety
  PositiveAff = 'PosAff', # positive affect
  NegativeAff = 'NegAff' # negative affect
)

# Initialize the results dataframe
results <- data.frame(Dependent_Variable = character(), 
                      Interaction_Effect = character(),
                      Control_Variable = character(),
                      Estimate = numeric(), 
                      P_Value = numeric(), 
                      stringsAsFactors = FALSE)

# Define pairs for interaction terms
interaction_pairs <- list(
  c("PRMQ1", "PHQ9"), 
  c("PRMQ1", "CESD"), 
  c("Confidence", "PHQ9"), 
  c("Confidence", "CESD"), 
  c("JOL", "PHQ9"), 
  c("JOL", "CESD")
)

# Outer loop for dependent variables
for (dep_var in dependent_vars) {
  
  # Loop for additional controls
  for (control_name in names(additional_controls)) {
    control_var <- additional_controls[[control_name]]
    
    # Loop through interaction pairs for interaction effects models
    for (pair in interaction_pairs) {
      interaction_var1 <- pair[1]
      interaction_var2 <- pair[2]
      
      # Construct the formula for the model with interaction terms ONLY
      formula_str_interaction <- paste("PMD$", dep_var, " ~ PMD$", interaction_var1, "* PMD$", interaction_var2, 
                                       " + PMD$Gender1 + PMD$Age + ", control_var, sep = "")
      
      # Run the model with interaction term only
      lm2 <- lm(as.formula(formula_str_interaction), data = PMD)
      summary_lm2 <- summary(lm2)
      
      # Extract estimate and p-value for the interaction term
      interaction_term <- paste("PMD$", interaction_var1, ":PMD$", interaction_var2, sep = "")
      estimate_interaction <- summary_lm2$coefficients[interaction_term, 1]  # Estimate for interaction
      p_value_interaction <- summary_lm2$coefficients[interaction_term, 4]   # P-value for interaction
      
      # Store the interaction model result
      results <- rbind(results, data.frame(Dependent_Variable = dep_var, 
                                           Interaction_Effect = paste(interaction_var1, "*", interaction_var2),
                                           Control_Variable = control_name,
                                           Estimate = estimate_interaction, 
                                           P_Value = p_value_interaction))
    }
  }
}

# Write the results to an Excel file
write.xlsx(results, file = "/Users/mickey.rice/Desktop/results_interactions_only.xlsx", rowNames = FALSE)

```

```{r}
# Low depression subset
low_dep <- PMD[PMD$PHQ9 <= 3, ]

describe(low_dep)

# High depression subset
high_dep <- PMD[PMD$PHQ9 >= 10, ]

describe(high_dep)

# Paired t-test
t_test_result1 <- t.test(low_dep$Accuracy, low_dep$JOL, paired = TRUE)

# View the result
print(t_test_result1)

# Paired t-test
t_test_result2 <- t.test(high_dep$Accuracy, high_dep$JOL, paired = TRUE)

# View the result
print(t_test_result2)

high_dep_women <- high_dep[high_dep$Gender == "Female", ]

# Paired t-test
t_test_result3 <- t.test(high_dep_women$Accuracy, high_dep_women$JOL, paired = TRUE)
print(t_test_result3)

```

