---
title: "Paper 1"
output: 
  html_notebook:
    toc: yes
  html_document:
    toc: yes
    df_print: paged
---

Created by Mickey Rice
October 8th, 2024

# Load Libaries 
```{r}
library(psych)
library(dplyr)
library(tidyverse)
library(apaTables)
library(ggplot2)

```

# Load Data 
```{r}
PMD <- read_csv("PMD.csv")
```

# Recode variables 
```{r}

PMD$Sex1<- 0
PMD$Sex1<-ifelse(PMD$Gender=="Male",-1, 1)


PMD$Gender1<- 0
PMD$Gender1<-ifelse(PMD$Gender=="Male", 0, 
                    ifelse(PMD$Gender=="Female", 1, 2))

## Explaining code : PM$Gender1<- 0 creates the new variable titled Gender1 
## PM$Gender1<-ifelse(PM$Gender ==“Male”,0 , ifelse(PM$Gender=="Female", 1, 2))) says “if the Gender is male, they will be 0, if Gender is female, they will be 1, if Gender is anything else it will be 2" 




# Gender1: Man = 0, Woman = 1. 
# Gender2: Women = 0, Transgender + nonbinary = 1. 
# Gender3: Men = 0, Transgender + nonbinary = 1.

```


```{r}
print(PMD)

describe(PMD)
```

# Print correlation tables
```{r}

#zero order correlation table 
desctable1 <- select(PMD, Accuracy, RT, PP, N300, PRMQ1, Confidence, JOL, Age, Gender1)

apa.cor.table(
      desctable1,
      filename = "desctablePaper1.doc",
      table.number = 1,
      show.conf.interval = TRUE,
      show.sig.stars = TRUE
)

#zero order correlation table 
desctable2 <- select(PMD, Accuracy, RT, PP, N300, PRMQ1, Confidence, JOL, Motivation, ADHD, HrsSleep, Sleepiness, Age, Gender1)

apa.cor.table(
      desctable2,
      filename = "desctable2Paper1.doc",
      table.number = 1,
      show.conf.interval = TRUE,
      show.sig.stars = TRUE,
      landscape = TRUE
)
```

# Sample info

```{r}
PMD %>%
  count(Gender)

PMD %>%
  count(Race)

PMD %>%
  count(Ethnicity)

PMD %>%
  count(Handedness)

describe(PMD$PRMQ1)

describe(PMD$Confidence)

describe(PMD$JOL)

describe(PMD$Accuracy)

describe(PMD$RT)
2093.87 - 282.68

describe(PMD$Motivation)
204 - 84

describe(PMD$ADHD)

describe(PMD$HrsSleep)

describe(PMD$Sleepiness)
```

# Regression of control variables on PMD variables

## Gender
```{r}

model <- lm(PRMQ1 ~ Gender1, data = PMD)
summary(model)

model <- lm(Confidence ~ Gender1, data = PMD)
summary(model)

model <- lm(JOL ~ Gender1, data = PMD)
summary(model)

model <- lm(Accuracy ~ Gender1, data = PMD)
summary(model)

model <- lm(RT ~ Gender1, data = PMD)
summary(model)

model <- lm(PP ~ Gender1, data = PMD)
summary(model)

model <- lm(N300 ~ Gender1, data = PMD)
summary(model)
```

## Age
```{r}
model <- lm(PRMQ1 ~ Age, data = PMD)
summary(model)

model <- lm(Confidence ~ Age, data = PMD)
summary(model)

model <- lm(JOL ~ Age, data = PMD)
summary(model)

model <- lm(Accuracy ~ Age, data = PMD)
summary(model)

model <- lm(RT ~ Age, data = PMD)
summary(model)

model <- lm(PP ~ Age, data = PMD)
summary(model)

model <- lm(N300 ~ Age, data = PMD)
summary(model)
```

# Correlations: Gender and age with variables
```{r}
# Gender

# Recode for point biserial correlations
PMD$GenderNew<- 0

PMD$GenderNew<-ifelse(PMD$Gender=="Male", "Man", 
                    ifelse(PMD$Gender=="Female", "Woman", "Trans"))

# df1: Man = 0, Woman = 1. 
df1 <- PMD[PMD$GenderNew %in% c("Man", "Woman"), ]
df1$GenderMW <- ifelse(df1$GenderNew == "Man", 0, 1)


# Loop through all the correlations!
dependent_vars <- c("Accuracy", "RT", "PP", "N300", "PRMQ1", "Confidence", "JOL", "Age")

# Initialize a list to store results
results <- list()

# Loop through each dependent variable
for (var in dependent_vars) {
    # Perform the correlation test
    correlation_result <- cor.test(df1$GenderMW, df1[[var]], method = "pearson")
    
    # Store the results in the list
    results[[var]] <- correlation_result
}

# Print the results
for (var in dependent_vars) {
    print(paste("Correlation results for:", var))
    print(results[[var]])
}

```

```{r}
# Recode for point biserial correlations
# df2: Women = 0, Transgender + nonbinary = 1. 
df2 <- PMD[PMD$GenderNew %in% c("Woman", "Trans"), ]
df2$GenderWT <- ifelse(df2$GenderNew == "Woman", 0, 1)


# Loop through all the correlations!
dependent_vars <- c("Accuracy", "RT", "PP", "N300", "PRMQ1", "Confidence", "JOL", "Age")

# Initialize a list to store results
results <- list()

# Loop through each dependent variable
for (var in dependent_vars) {
    # Perform the correlation test
    correlation_result <- cor.test(df2$GenderWT, df2[[var]], method = "pearson")
    
    # Store the results in the list
    results[[var]] <- correlation_result
}

# Print the results
for (var in dependent_vars) {
    print(paste("Correlation results for:", var))
    print(results[[var]])
}
```

```{r}
# Recode for point biserial correlations
# df3: Men = 0, Transgender + nonbinary = 1.
df3 <- PMD[PMD$GenderNew %in% c("Man", "Trans"), ]
df3$GenderMT <- ifelse(df3$GenderNew == "Man", 0, 1)


# Loop through all the correlations!
dependent_vars <- c("Accuracy", "RT", "PP", "N300", "PRMQ1", "Confidence", "JOL", "Age")

# Initialize a list to store results
results <- list()

# Loop through each dependent variable
for (var in dependent_vars) {
    # Perform the correlation test
    correlation_result <- cor.test(df3$GenderMT, df3[[var]], method = "pearson")
    
    # Store the results in the list
    results[[var]] <- correlation_result
}

# Print the results
for (var in dependent_vars) {
    print(paste("Correlation results for:", var))
    print(results[[var]])
}

```

# Regression: Metamemtory predicting Accuracy controlling for age and gender
```{r}
# scale = standardizing the coefficients 

fit4 <- lm(scale(Accuracy) ~ scale(PRMQ1) + Age + Gender1, data = PMD)
summary(fit4)

fit5 <- lm(scale(Accuracy) ~ scale(Confidence) + Age + Gender1, data = PMD)
summary(fit5)

fit6 <- lm(scale(Accuracy) ~ scale(JOL) + Age + Gender1, data = PMD)
summary(fit6)

```

# Regression: Metamemtory predicting RT controlling for age and gender
```{r}
## scale = standardizing the coefficients 

fit4 <- lm(scale(RT) ~ scale(PRMQ1) + Gender1 + Age, data = PMD)
summary(fit4)

fit5 <- lm(scale(RT) ~ scale(Confidence) + Gender1 + Age, data = PMD)
summary(fit5)

fit6 <- lm(scale(RT) ~ scale(JOL) + Gender1 + Age, data = PMD)
summary(fit6)
```

# Regression: Metamemtory predicting N300 controlling for age and gender
```{r}
## scale = standardizing the coefficients 

fit4 <- lm(scale(N300) ~ scale(PRMQ1) + Gender1 + Age, data = PMD)
summary(fit4)

fit5 <- lm(scale(N300) ~ scale(Confidence) + Gender1 + Age, data = PMD)
summary(fit5)

fit6 <- lm(scale(N300) ~ scale(JOL) + Gender1 + Age, data = PMD)
summary(fit6)
```

# Regression: Metamemtory predicting PP controlling for age and gender
```{r}
## scale = standardizing the coefficients 

fit4 <- lm(scale(PP) ~ scale(PRMQ1) + Gender1 + Age, data = PMD)
summary(fit4)

fit5 <- lm(scale(PP) ~ scale(Confidence) + Gender1 + Age, data = PMD)
summary(fit5)

fit6 <- lm(scale(PP) ~ scale(JOL) + Gender1 + Age, data = PMD)
summary(fit6)
```

# Effect sizes 
## Partial R-squared for PRMQ1 on Accuracy
```{r}
#full linear regression model
full_model <- lm(Accuracy ~ PRMQ1 + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(Accuracy ~ Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## Partial R-squared for Confidence on RT
```{r}
#full linear regression model
full_model <- lm(RT ~ Confidence + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(RT ~ Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## Partial R-squared for JOL on RT
```{r}
#full linear regression model
full_model <- lm(RT ~ JOL + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(RT ~ Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## Partial R-squared for PRMQ1 on PP
```{r}
#full linear regression model
full_model <- lm(PP ~ PRMQ1 + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(PP ~ Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## Partial R-squared for Confidence on PP
```{r}
#full linear regression model
full_model <- lm(PP ~ Confidence + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(PP ~ Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## Non significant effect sizes
```{r}
#full linear regression model
full_model <- lm(N300 ~ JOL + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(N300 ~ Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)

```


# Exploratory
## SES

# Averaging SES
```{r}
PMD$pared1 <- as.numeric(as.character(PMD$pared1))
PMD$pared2 <- as.numeric(as.character(PMD$pared2))

PMD <- PMD %>%
  mutate(avgpared = rowMeans(select(., pared1, pared2), na.rm = TRUE))

# View the updated dataframe
print(PMD)

describe(PMD)

```

```{r}

model <- lm(PRMQ1 ~ avgpared, data = PMD)
summary(model)

model <- lm(Confidence ~ avgpared, data = PMD)
summary(model)

model <- lm(JOL ~ avgpared, data = PMD)
summary(model)

model <- lm(Accuracy ~ avgpared, data = PMD)
summary(model)

model <- lm(RT ~ avgpared, data = PMD)
summary(model)

model <- lm(PP ~ avgpared, data = PMD)
summary(model)

model <- lm(N300 ~ avgpared, data = PMD)
summary(model)

```

Hours of sleep
```{r}
model <- lm(PRMQ1 ~ HrsSleep, data = PMD)
summary(model)

model <- lm(Confidence ~ HrsSleep, data = PMD)
summary(model)

model <- lm(JOL ~ HrsSleep, data = PMD)
summary(model)

model <- lm(Accuracy ~ HrsSleep, data = PMD)
summary(model)

model <- lm(RT ~ HrsSleep, data = PMD)
summary(model)

model <- lm(PP ~ HrsSleep, data = PMD)
summary(model)

model <- lm(N300 ~ HrsSleep, data = PMD)
summary(model)


```

Sleepiness
```{r}
model <- lm(PRMQ1 ~ Sleepiness, data = PMD)
summary(model)

model <- lm(Confidence ~ Sleepiness, data = PMD)
summary(model)

model <- lm(JOL ~ Sleepiness, data = PMD)
summary(model)

model <- lm(Accuracy ~ Sleepiness, data = PMD)
summary(model)

model <- lm(RT ~ Sleepiness, data = PMD)
summary(model)

model <- lm(PP ~ Sleepiness, data = PMD)
summary(model)

model <- lm(N300 ~ Sleepiness, data = PMD)
summary(model)

```

## Motivation
```{r}

model <- lm(PRMQ1 ~ Motivation, data = PMD)
summary(model)

model <- lm(Confidence ~ Motivation, data = PMD)
summary(model)

model <- lm(JOL ~ Motivation, data = PMD)
summary(model)

model <- lm(Accuracy ~ Motivation, data = PMD)
summary(model)

model <- lm(RT ~ Motivation, data = PMD)
summary(model)

model <- lm(PP ~ Motivation, data = PMD)
summary(model)

model <- lm(N300 ~ Motivation, data = PMD)
summary(model)

```

## ADHD
```{r}

model <- lm(PRMQ1 ~ ADHD, data = PMD)
summary(model)

model <- lm(Confidence ~ ADHD, data = PMD)
summary(model)

model <- lm(JOL ~ ADHD, data = PMD)
summary(model)

model <- lm(Accuracy ~ ADHD, data = PMD)
summary(model)

model <- lm(RT ~ ADHD, data = PMD)
summary(model)

model <- lm(PP ~ ADHD, data = PMD)
summary(model)

model <- lm(N300 ~ ADHD, data = PMD)
summary(model)

```

## Make a scatterplot:Metamemory (PRMQ1) & PM Accuracy
```{r}
p <- ggplot(PMD, aes(x = PRMQ1, y = Accuracy)) +
  geom_point() +
    geom_smooth(method = "lm", se=FALSE, fullrange=TRUE, color = "black") + theme_minimal() + scale_color_grey()
p <- p + ggtitle("") + xlab("Self-Evaluation of Prospective Memory Failures") + ylab("Prospective Memory Accuracy") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.text=element_text(size=18),
        axis.title=element_text(size=18,face="plain"))
p

ggsave("PRMQ1_Accuracy", path = '/Users/mickey.rice/Desktop/', bg="white", width = 7, height = 7, device='jpeg', dpi= 700)

```

## Make a scatterplot:Metamemory (PRMQ1) & PP
```{r}
p <- ggplot(PMD, aes(x = PRMQ1, y = PP)) +
  geom_point() +
    geom_smooth(method = "lm", se=FALSE, fullrange=TRUE, color = "black") + theme_minimal() + scale_color_grey()
p <- p + ggtitle("") + xlab("Self-Evaluation of Prospective Memory Failures") + ylab("Prospective Positivity (mV)") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.text=element_text(size=18),
        axis.title=element_text(size=18,face="plain"))
p

ggsave("PRMQ1_PP", path = '/Users/mickey.rice/Desktop/', bg="white", width = 7, height = 7, device='jpeg', dpi= 700)
```

## Make a scatterplot:Metamemory (Confidence) & RT
```{r}
p <- ggplot(PMD, aes(x = Confidence, y = RT)) +
  geom_point() +
    geom_smooth(method = "lm", se=FALSE, fullrange=TRUE, color = "black") + theme_minimal() + scale_color_grey()
p <- p + ggtitle("") + xlab("Self-Reports of Poor Cognitive Confidence") + ylab("Reaction Time (ms)") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.text=element_text(size=18),
        axis.title=element_text(size=18,face="plain"))

p

ggsave("Confidence_RT", path = '/Users/mickey.rice/Desktop/', bg="white", width = 7, height = 7, device='jpeg', dpi= 700)
```

## Make a scatterplot:Metamemory (Confidence) & PP
```{r}
ggplot(PMD, aes(x = Confidence, y = PP)) +
  geom_point() +
    geom_smooth(method = "lm", color = "dark green") +
  labs(
       x="Confidence Score", y = "Prospective Positivity (mV)")+
  theme_classic()  +
  theme(text = element_text(size = 18))                    
```

## Make a scatterplot:Metamemory (JOL) & RT
```{r}
p <- ggplot(PMD, aes(x = JOL, y = RT)) +
  geom_point() +
    geom_smooth(method = "lm", se=FALSE, fullrange=TRUE, color = "black") + theme_minimal() + scale_color_grey()
p <- p + ggtitle("") + xlab("Performance Predictions") + ylab("Reaction Time (ms)") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.text=element_text(size=18),
        axis.title=element_text(size=18,face="plain"))
p

ggsave("JOL_RT", path = '/Users/mickey.rice/Desktop/', bg="white", width = 7, height = 7, device='jpeg', dpi= 700)
```

## Make a scatterplot:Metamemory (JOL) & RT
```{r}
p <- ggplot(PMD, aes(x = JOL, y = Accuracy)) +
  geom_point() +
    geom_smooth(method = "lm", se=FALSE, fullrange=TRUE, color = "black") + theme_minimal() + scale_color_grey()
p <- p + ggtitle("") + xlab("Performance Predictions (%)") + ylab("Accuracy (%)") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20,face="plain"))
p

ggsave("JOL_Acc", path = '/Users/mickey.rice/Desktop/', bg="white", width = 5, height = 5, device='jpeg', dpi= 700)
```

# Exploratory: test to see if there is a significant difference between the predicted and actual accuracy
```{r}
# Paired t-test
t_test_result <- t.test(PMD$Accuracy, PMD$JOL, paired = TRUE)

# View the result
print(t_test_result)
```


# Sensitivity analyses
```{r}
library(openxlsx)

# List of dependent variables
dependent_vars <- c('Accuracy', 'RT', 'PP', 'N300')

# Independent variables to be tested sequentially
selected_columns <- c('PRMQ1', 'Confidence', 'JOL')

# List of additional controls
additional_controls <- list(
  SES = "PMD$avgpared",       # Socioeconomic status
  ADHD = "PMD$ADHD",     # ADHD symptoms
  Motivation = "PMD$Motivation", # motivation score
  Sleepiness = "PMD$Sleepiness", # Sleepiness score
  HrsSleep = "PMD$HrsSleep" # Hours of sleep the night before
)

# Initialize the results dataframe
results <- data.frame(Dependent_Variable = character(), 
                      Independent_Variable = character(), 
                      Control_Variable = character(),
                      Estimate = numeric(), 
                      P_Value = numeric(), 
                      stringsAsFactors = FALSE)

# Outer loop for dependent variables
for (dep_var in dependent_vars) {
  
  # Inner loop for independent variables (tested sequentially)
  for (col in selected_columns) {
    
    # Loop for additional controls
    for (control_name in names(additional_controls)) {
      control_var <- additional_controls[[control_name]]
      
      # Construct the formula for each model
      formula_str <- paste("PMD$", dep_var, " ~ PMD$", col, " + PMD$Gender1 + PMD$Age + ", control_var, sep = "")
      
      # Run the linear model
      lm1 <- lm(as.formula(formula_str), data = PMD)
      summary_lm1 <- summary(lm1)
      
      # Extract estimate and p-value for the variable of interest (col)
      estimate <- summary_lm1$coefficients[2, 1]  # 2nd row, 1st column (estimate)
      p_value <- summary_lm1$coefficients[2, 4]   # 2nd row, 4th column (p-value)
      
      # Store the result in the results dataframe
      results <- rbind(results, data.frame(Dependent_Variable = dep_var, 
                                           Independent_Variable = col, 
                                           Control_Variable = control_name,
                                           Estimate = estimate, 
                                           P_Value = p_value))
    }
  }
}

# Write the results to an Excel file
write.xlsx(results, file = "/Users/mickey.rice/Desktop/results1.xlsx", rowNames = FALSE)
```



```{r}
library(openxlsx)

# List of dependent variables
dependent_vars <- c('Accuracy', 'RT')

# Independent variables to be tested sequentially
selected_columns <- c('PHQ9', 'CESD', 'PP', 'N300')

# List of additional controls
additional_controls <- list(
  SES = "PMD$avgpared",       # Socioeconomic status
  ADHD = "PMD$ADHD",     # ADHD symptoms
  Motivation = "PMD$Motivation", # motivation score
  Sleepiness = "PMD$Sleepiness", # Sleepiness score
  HrsSleep = "PMD$HrsSleep", # Hours of sleep the night before
    Anxiety = 'STAIS', # State anxiety levels
  PositiveAff = 'PosAff', # positive affect
  NegativeAff = 'NegAff' # negative affect
)

# Initialize the results dataframe
results <- data.frame(Dependent_Variable = character(), 
                      Independent_Variable = character(), 
                      Control_Variable = character(),
                      Estimate = numeric(), 
                      P_Value = numeric(), 
                      stringsAsFactors = FALSE)

# Outer loop for dependent variables
for (dep_var in dependent_vars) {
  
  # Inner loop for independent variables (tested sequentially)
  for (col in selected_columns) {
    
    # Loop for additional controls
    for (control_name in names(additional_controls)) {
      control_var <- additional_controls[[control_name]]
      
      # Construct the formula for each model
      formula_str <- paste("PMD$", dep_var, " ~ PMD$", col, " + PMD$Gender1 + PMD$Age + ", control_var, sep = "")
      
      # Run the linear model
      lm1 <- lm(as.formula(formula_str), data = PMD)
      summary_lm1 <- summary(lm1)
      
      # Extract estimate and p-value for the variable of interest (col)
      estimate <- summary_lm1$coefficients[2, 1]  # 2nd row, 1st column (estimate)
      p_value <- summary_lm1$coefficients[2, 4]   # 2nd row, 4th column (p-value)
      
      # Store the result in the results dataframe
      results <- rbind(results, data.frame(Dependent_Variable = dep_var, 
                                           Independent_Variable = col, 
                                           Control_Variable = control_name,
                                           Estimate = estimate, 
                                           P_Value = p_value))
    }
  }
}

# Write the results to an Excel file
write.xlsx(results, file = "/Users/mickey.rice/Desktop/results3.xlsx", rowNames = FALSE)
```

# Extra graph info 

Paper 1-------------------------------------------------------------------------

## Make a scatterplot:Metamemory (PRMQ1) & PM Accuracy
```{r}
ggplot(PMD, aes(x = PRMQ1, y = Accuracy)) +
  geom_point() +
    geom_smooth(method = "lm", color = "dark green") +
  labs(title="Metamemory Predicting Prospective Memory Accuracy",
       x="PRMQ Score", y = "Accuracy")+
  theme_classic()  +
  theme(text = element_text(size = 16))                    
```


## Make a scatterplot:Metamemory (PRMQ1) & PP
```{r}
ggplot(PMD, aes(x = PRMQ1, y = PP)) +
  geom_point() +
    geom_smooth(method = "lm", color = "dark green") +
  labs(
       x="PRMQ Score", y = "Prospective Positivity Amplitude (mV)")+
  theme_classic()  +
  theme(text = element_text(size = 18))                    
```


## Make a scatterplot:Metamemory (PRMQ1) & N300
```{r}
ggplot(PMD, aes(x = PRMQ1, y = N300)) +
  geom_point() +
    geom_smooth(method = "lm", color = "dark green") +
  labs(title="Metamemory Predicting Cue Detection",
       x="PRMQ Score", y = "N300 Amplitude (mV)")+
  theme_classic()  +
  theme(text = element_text(size = 18))                    
```

# No covariates
# Regression: Metamemtory predicting Accuracy
```{r}
# scale = standardizing the coefficients 

fit4 <- lm(scale(Accuracy) ~ scale(PRMQ1), data = PMD)
summary(fit4)

fit5 <- lm(scale(Accuracy) ~ scale(Confidence), data = PMD)
summary(fit5)

fit6 <- lm(scale(Accuracy) ~ scale(JOL), data = PMD)
summary(fit6)

```

# Regression: Metamemtory predicting RT 
```{r}
## scale = standardizing the coefficients 

fit4 <- lm(scale(RT) ~ scale(PRMQ1), data = PMD)
summary(fit4)

fit5 <- lm(scale(RT) ~ scale(Confidence), data = PMD)
summary(fit5)

fit6 <- lm(scale(RT) ~ scale(JOL), data = PMD)
summary(fit6)
```

# Regression: Metamemtory predicting N300 
```{r}
## scale = standardizing the coefficients 

fit4 <- lm(scale(N300) ~ scale(PRMQ1), data = PMD)
summary(fit4)

fit5 <- lm(scale(N300) ~ scale(Confidence), data = PMD)
summary(fit5)

fit6 <- lm(scale(N300) ~ scale(JOL), data = PMD)
summary(fit6)
```

# Regression: Metamemtory predicting PP
```{r}
## scale = standardizing the coefficients 

fit4 <- lm(scale(PP) ~ scale(PRMQ1), data = PMD)
summary(fit4)

fit5 <- lm(scale(PP) ~ scale(Confidence), data = PMD)
summary(fit5)

fit6 <- lm(scale(PP) ~ scale(JOL), data = PMD)
summary(fit6)
```

