---
title: "Paper 3"
output: 
  html_notebook:
    toc: yes
  html_document:
    toc: yes
    df_print: paged
---

Created by Mickey Rice
October 7th, 2024


# Load Libaries 
```{r}
#install.packages("car")
#install.packages("lsr")
#install.packages("MBESS")

#library(car)
#library(lsr)
#library(MBESS)
library(psych)
library(tidyverse)
library(apaTables)
```

# Load Data 
```{r}
PMD <- read_csv("PMD.csv")
```


# Recode variables 
```{r}

PMD$Sex1<- 0
PMD$Sex1<-ifelse(PMD$Gender=="Male",-1, 1)


PMD$Gender1<- 0
PMD$Gender1<-ifelse(PMD$Gender=="Male", 0, 
                    ifelse(PMD$Gender=="Female", 1, 2))

## Explaining code : PM$Gender1<- 0 creates the new variable titled Gender1 
## PM$Gender1<-ifelse(PM$Gender ==“Male”,0 , ifelse(PM$Gender=="Female", 1, 2))) says “if the Gender is male, they will be 0, if Gender is female, they will be 1, if Gender is anything else it will be 2" 

```



```{r}
PMD_Describe <- describe(PMD)
PMD_Describe
```
# Check to see if the missing values are at random or not
```{r}
# install.packages("naniar")
library(naniar)

# Perform MCAR test
mcar_result <- mcar_test(PMD)

# Display the results
print(mcar_result)
```


# Missing values
```{r}

# Replace missing Race values with "Do not wish to respond"
PMD$Race[is.na(PMD$Race)] <- "Do not wish to respond"

PMD_Describe <- describe(PMD)
PMD_Describe
```

# Correlation tables
```{r}
library(apaTables)

# for Paper 3
desctable3 <- select(PMD, Accuracy, RT, PP, N300, PRMQ1, Confidence, JOL, PHQ9, CESD, Age, Gender1)

apa.cor.table(
      desctable3,
      filename = "desctablePaper3.doc",
      table.number = 2,
      show.conf.interval = TRUE,
      show.sig.stars = TRUE,
      landscape = TRUE
)

#zero order correlation table 
desctable2 <- select(PMD, Accuracy, RT, PP, N300, PRMQ1, Confidence, JOL, Motivation, ADHD, HrsSleep, Sleepiness, PosAff, NegAff, STAIS)

apa.cor.table(
      desctable2,
      filename = "desctable2Paper3.doc",
      table.number = 1,
      show.conf.interval = TRUE,
      show.sig.stars = TRUE,
      landscape = TRUE
)

```

```{r}
# Gender

# Recode for point biserial correlations
PMD$GenderNew<- 0

PMD$GenderNew<-ifelse(PMD$Gender=="Male", "Man", 
                    ifelse(PMD$Gender=="Female", "Woman", "Trans"))

# df1: Man = 0, Woman = 1. 
df1 <- PMD[PMD$GenderNew %in% c("Man", "Woman"), ]
df1$GenderMW <- ifelse(df1$GenderNew == "Man", 0, 1)


# Loop through all the correlations!
dependent_vars <- c("Accuracy", "RT", "PP", "N300", "PRMQ1", "Confidence", "JOL", "PHQ9", "CESD", "Age")

# Initialize a list to store results
results <- list()

# Loop through each dependent variable
for (var in dependent_vars) {
    # Perform the correlation test
    correlation_result <- cor.test(df1$GenderMW, df1[[var]], method = "pearson")
    
    # Store the results in the list
    results[[var]] <- correlation_result
}

# Print the results
for (var in dependent_vars) {
    print(paste("Correlation results for:", var))
    print(results[[var]])
}

```

```{r}
# Recode for point biserial correlations
# df2: Women = 0, Transgender + nonbinary = 1. 
df2 <- PMD[PMD$GenderNew %in% c("Woman", "Trans"), ]
df2$GenderWT <- ifelse(df2$GenderNew == "Woman", 0, 1)


# Loop through all the correlations!
dependent_vars <- c("Accuracy", "RT", "PP", "N300", "PRMQ1", "Confidence", "JOL", "PHQ9", "CESD", "Age")

# Initialize a list to store results
results <- list()

# Loop through each dependent variable
for (var in dependent_vars) {
    # Perform the correlation test
    correlation_result <- cor.test(df2$GenderWT, df2[[var]], method = "pearson")
    
    # Store the results in the list
    results[[var]] <- correlation_result
}

# Print the results
for (var in dependent_vars) {
    print(paste("Correlation results for:", var))
    print(results[[var]])
}
```

```{r}
# Recode for point biserial correlations
# df3: Men = 0, Transgender + nonbinary = 1.
df3 <- PMD[PMD$GenderNew %in% c("Man", "Trans"), ]
df3$GenderMT <- ifelse(df3$GenderNew == "Man", 0, 1)


# Loop through all the correlations!
dependent_vars <- c("Accuracy", "RT", "PP", "N300", "PRMQ1", "Confidence", "JOL", "PHQ9", "CESD", "Age")

# Initialize a list to store results
results <- list()

# Loop through each dependent variable
for (var in dependent_vars) {
    # Perform the correlation test
    correlation_result <- cor.test(df3$GenderMT, df3[[var]], method = "pearson")
    
    # Store the results in the list
    results[[var]] <- correlation_result
}

# Print the results
for (var in dependent_vars) {
    print(paste("Correlation results for:", var))
    print(results[[var]])
}

```

## Centering the variables for an interaction
```{r}
## centering the variable - most important for interaction
PHQ9 <- PMD$PHQ9
mean_PHQ9 <- mean(PHQ9)
PHQ9_c <- PHQ9 - mean_PHQ9
PMD$PHQ9_c <- PHQ9_c

CESD <- PMD$CESD
mean_CESD <- mean(CESD)
CESD_c <- CESD - mean_CESD
PMD$CESD_c <- CESD_c

DASS <- PMD$DASS
mean_DASS <- mean(DASS)
DASS_c <- DASS - mean_DASS
PMD$DASS_c <- DASS_c

PRMQ1 <- PMD$PRMQ1
mean_PRMQ1 <- mean(PRMQ1)
PRMQ1_c <- PRMQ1 - mean_PRMQ1
PMD$PRMQ1_c <- PRMQ1_c

Confidence <- PMD$Confidence
mean_Confidence <- mean(Confidence)
Confidence_c <- Confidence - mean_Confidence
PMD$Confidence_c <- Confidence_c

JOL <- PMD$JOL
mean_JOL <- mean(JOL)
JOL_c <- JOL - mean_JOL
PMD$JOL_c <- JOL_c


N300 <- PMD$N300
mean_N300 <- mean(N300)
N300_c <- N300 - mean_N300
PMD$N300_c <- N300_c

PP <- PMD$PP
mean_PP <- mean(PP)
PP_c <- PP - mean_PP
PMD$PP_c <- PP_c

fitInt <- lm(Accuracy ~ N300_c * PRMQ1_c + Gender1 + Age, data = PMD)
summary(fitInt)

# PM$Gender1_f <- as.factor(PM$Gender1)

# contrasts(PM$Gender1_f) <- contr.helmert(n = 3)

```

# Regression main effects-------------------------------------------------------

## Regression: Depression predicting Accuracy controlling for age and gender
```{r}
## scale = standardizing the coefficients 

fit1 <- lm(scale(Accuracy) ~ scale(PHQ9)+ Age + Gender1, data = PMD)
summary(fit1)

fit2 <- lm(scale(Accuracy) ~ scale(CESD) + Age + Gender1, data = PMD)
summary(fit2)

# fit3 <- lm(scale(Accuracy) ~ scale(DASS) + Age + Gender1, data = PMD)
# summary(fit3)
```

## Regression: Depression predicting RT controlling for age and gender
```{r}
## scale = standardizing the coefficients 

fit1 <- lm(scale(RT) ~ scale(PHQ9) + Gender1 + Age, data = PMD)
summary(fit1)

fit2 <- lm(scale(RT) ~ scale(CESD) + Gender1 + Age, data = PMD)
summary(fit2)

# fit3 <- lm(scale(RT) ~ scale(DASS) + Gender1 + Age, data = PMD)
# summary(fit3)
```

## Regression: N300 predicting Accuracy and RT controlling for age and gender
```{r}
## scale = standardizing the coefficients 

fit1 <- lm(scale(Accuracy) ~ scale(N300) + Gender1 + Age, data = PMD)
summary(fit1)

fit2 <- lm(scale(RT) ~ scale(N300) + Gender1 + Age, data = PMD)
summary(fit2)
```

## Regression: PP predicting Accuracy and RT controlling for age and gender
```{r}
## scale = standardizing the coefficients 

fit1 <- lm(scale(Accuracy) ~ scale(PP) + Gender1 + Age, data = PMD)
summary(fit1)

fit2 <- lm(scale(RT) ~ scale(PP) + Gender1 + Age, data = PMD)
summary(fit2)

```

# Mediation---------------------------------------------------------------------

##Original proposal: PHQ9 for depression, N300 as mediator - doesn't make sense because no b path!
```{r}
# PHQ9 -> N300 -> Accuracy

#install.packages("mediation")
#install.packages("minqa")
#library(mediation)

model.M <- lm(N300 ~ PHQ9 + Gender1 + Age, data = PMD)
model.Y <- lm(Accuracy ~ N300 + PHQ9 + Gender1 + Age, data =PMD)
results <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "PHQ9", 
                              mediator= 'N300', 
                              boot=TRUE, sims=10000)
summary(results)
```

## Exploratory interaction for metamemory as moderatory still!
### Second stage moderators
```{r}
# N300 *PRMQ  accuracy
lm <- lm(Accuracy ~ N300_c * PRMQ1_c + Age + Gender1, PMD)
summary(lm)

# N300 * confidence  accuracy
lm <- lm(Accuracy ~ N300_c * Confidence_c + Age + Gender1, PMD)
summary(lm)

# N300 * predictions  accuracy
lm <- lm(Accuracy ~ N300_c * JOL_c + Age + Gender1, PMD)
summary(lm)

# PP*PRMQ  accuracy
lm <- lm(Accuracy ~ PP_c * PRMQ1_c + Age + Gender1, PMD)
summary(lm)

# PP* confidence  accuracy
lm <- lm(Accuracy ~ PP_c * Confidence_c + Age + Gender1, PMD)
summary(lm)

# PP * predictions  accuracy
lm <- lm(Accuracy ~ PP_c * JOL_c + Age + Gender1, PMD)
summary(lm)
```

### Direct effect moderator: use in exploratory moderated mediation 
```{r}
# N300 * PHQ9  accuracy
lm <- lm(Accuracy ~ N300_c * PHQ9_c + Age + Gender1, PMD)
summary(lm)

# N300 * CESD  accuracy
lm <- lm(Accuracy ~ N300_c * CESD_c + Age + Gender1, PMD)
summary(lm)

# PP * PHQ9  accuracy
lm <- lm(Accuracy ~ PP_c * PHQ9_c + Age + Gender1, PMD)
summary(lm)

# PP * CESD  accuracy
lm <- lm(Accuracy ~ PP_c * CESD_c + Age + Gender1, PMD)
summary(lm)

```

## Moderated Mediation Analyses: ERPs as Moderator
###First Stage Moderation
```{r}
# PP on PHQ9 and PRMQ.
lm <- lm(PRMQ1 ~ PP_c*PHQ9_c + Age + Gender1, PMD)
summary(lm)
# N300 on PHQ9 and PRMQ.
lm <- lm(PRMQ1 ~ N300_c*PHQ9_c + Age + Gender1, PMD)
summary(lm)
# PP on CESD and PRMQ. 
lm <- lm(PRMQ1 ~ PP_c*CESD_c + Age + Gender1, PMD)
summary(lm)
# N300 on CESD and PRMQ. 
lm <- lm(PRMQ1 ~ N300_c*CESD_c + Age + Gender1, PMD)
summary(lm)

```




## Exploratory mediation!

## PHQ9 for depression, PRMQ1 as mediator (not proposed, but makes sense!)
```{r}
# PHQ9 -> PRMQ1 -> Accuracy

#install.packages("mediation")
#install.packages("minqa")
#library(mediation)

model.M <- lm(PRMQ1 ~ PHQ9 + Gender1 + Age, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + PHQ9 + Gender1 + Age, data =PMD)
results <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "PHQ9", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(results)

# Extract standard error 
se_indirect_c <- sd(results$d0.sims) # Standard error for indirect effect
se_direct_c <- sd(results$z0.sims)   # Standard error for direct effect
se_total_c <- sd(results$tau.sims)   # Standard error for total effect

# Display results
cat("Standard Errors (PHQ9):", "\nIndirect:", se_indirect_c, "\nDirect:", se_direct_c, "\nTotal:", se_total_c, "\n")
```

## Create APA formatted table
```{r}
# Extract effect estimates, confidence intervals, standard errors, and p-values
indirect_effect <- results$d0
indirect_ci <- c(results$d0.ci[1], results$d0.ci[2])
indirect_se <- sd(results$d0.sims)
indirect_p <- results$d0.p

direct_effect <- results$z0
direct_ci <- c(results$z0.ci[1], results$z0.ci[2])
direct_se <- sd(results$z0.sims)
direct_p <- results$z0.p

total_effect <- results$tau.coef
total_ci <- c(results$tau.ci[1], results$tau.ci[2])
total_se <- sd(results$tau.sims)
total_p <- results$tau.p

# Create data frame with all values
results_table <- data.frame(
  Effect = c("Indirect", "Direct", "Total"),
  Estimate = c(indirect_effect, direct_effect, total_effect),
  SE = c(indirect_se, direct_se, total_se),
  `CI Lower` = c(indirect_ci[1], direct_ci[1], total_ci[1]),
  `CI Upper` = c(indirect_ci[2], direct_ci[2], total_ci[2]),
  `p-value` = c(indirect_p, direct_p, total_p)
)

# install.packages("kableExtra")
# install.packages("officer")
library(officer)
library(kableExtra)

# Create APA-style table
results_table %>%
  kable("html", caption = "Mediation Analysis Results") %>%
  kable_styling(full_width = FALSE, position = "center") %>%
  add_header_above(c(" " = 1, "Estimate" = 1, "Standard Error" = 1, "95% Confidence Interval" = 2, " " = 1)) %>%
  column_spec(2, bold = TRUE) %>%
  footnote(general = "Estimates, standard errors, confidence intervals, and p-values for the indirect, direct, and total effects.",
           general_title = "Note: ")

library(officer)
library(kableExtra)

# Create APA-style table in HTML format
results_html_table <- results_table %>%
  kable("html", caption = "Model Results for PHQ-9 Relating to PM Accuracy via PM-related Metamemory  Beliefs (PRMQ) while controlling for age and gender") %>%
  kable_styling(full_width = FALSE, position = "center") %>%
  add_header_above(c(" " = 1, "Standardized Beta" = 1, "Standard Error" = 1, "95% Confidence Interval" = 2, " " = 1)) %>%
  column_spec(2, bold = TRUE) %>%
  footnote(general = "Standardized Betas, standard errors, confidence intervals, and p-values for the indirect, direct, and total effects.",
           general_title = "Note: ")

# Create a new Word document
doc <- read_docx()

# Add the table to the Word document
doc <- doc %>%
  body_add_par("Model Results for PHQ-9 Relating to PM Accuracy via PM-related Metamemory  Beliefs (PRMQ) while controlling for age and gender", style = "heading 1") %>%
  body_add_table(value = results_table, style = "table_template") %>%  # You can define a style template in Word if you prefer
  body_add_par("Note: Standardized Betas, standard errors, confidence intervals, and p-values for the indirect, direct, and total effects.", style = "Normal")

# Save the document
print(doc, target = "PHQ9_agegender_Mediation_Analysis_Results.docx")

```



## CESD for depression, PRMQ1 as mediator 
```{r}
# CESD -> PRMQ1 -> Accuracy

#install.packages("mediation")
#install.packages("minqa")
#library(mediation)

model.M <- lm(PRMQ1 ~ CESD + Gender1 + Age, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + CESD + Gender1 + Age, data =PMD)
results <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "CESD", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(results)


```

## Create APA formatted table
```{r}
# Extract effect estimates, confidence intervals, standard errors, and p-values
indirect_effect <- results$d0
indirect_ci <- c(results$d0.ci[1], results$d0.ci[2])
indirect_se <- sd(results$d0.sims)
indirect_p <- results$d0.p

direct_effect <- results$z0
direct_ci <- c(results$z0.ci[1], results$z0.ci[2])
direct_se <- sd(results$z0.sims)
direct_p <- results$z0.p

total_effect <- results$tau.coef
total_ci <- c(results$tau.ci[1], results$tau.ci[2])
total_se <- sd(results$tau.sims)
total_p <- results$tau.p

# Create data frame with all values
results_table <- data.frame(
  Effect = c("Indirect", "Direct", "Total"),
  Estimate = c(indirect_effect, direct_effect, total_effect),
  SE = c(indirect_se, direct_se, total_se),
  `CI Lower` = c(indirect_ci[1], direct_ci[1], total_ci[1]),
  `CI Upper` = c(indirect_ci[2], direct_ci[2], total_ci[2]),
  `p-value` = c(indirect_p, direct_p, total_p)
)

# install.packages("kableExtra")
# install.packages("officer")
library(officer)
library(kableExtra)

# Create APA-style table
results_table %>%
  kable("html", caption = "Mediation Analysis Results") %>%
  kable_styling(full_width = FALSE, position = "center") %>%
  add_header_above(c(" " = 1, "Estimate" = 1, "Standard Error" = 1, "95% Confidence Interval" = 2, " " = 1)) %>%
  column_spec(2, bold = TRUE) %>%
  footnote(general = "Estimates, standard errors, confidence intervals, and p-values for the indirect, direct, and total effects.",
           general_title = "Note: ")

library(officer)
library(kableExtra)

# Create APA-style table in HTML format
results_html_table <- results_table %>%
  kable("html", caption = "Model Results for CES-D Relating to PM Accuracy via PM-related Metamemory  Beliefs (PRMQ) while controlling for age and gender") %>%
  kable_styling(full_width = FALSE, position = "center") %>%
  add_header_above(c(" " = 1, "Standardized Beta" = 1, "Standard Error" = 1, "95% Confidence Interval" = 2, " " = 1)) %>%
  column_spec(2, bold = TRUE) %>%
  footnote(general = "Standardized Betas, standard errors, confidence intervals, and p-values for the indirect, direct, and total effects.",
           general_title = "Note: ")

# Create a new Word document
doc <- read_docx()

# Add the table to the Word document
doc <- doc %>%
  body_add_par("Model Results for CES-D Relating to PM Accuracy via PM-related Metamemory  Beliefs (PRMQ) while controlling for age and gender", style = "heading 1") %>%
  body_add_table(value = results_table, style = "table_template") %>%  # You can define a style template in Word if you prefer
  body_add_par("Note: Standardized Betas, standard errors, confidence intervals, and p-values for the indirect, direct, and total effects.", style = "Normal")

# Save the document
print(doc, target = "CESD_agegender_Mediation_Analysis_Results.docx")

```

# Moderated Mediation (mediate package)-----------------------------------------

## Original proposal: Using the mediate package: PHQ9 for depression, N300 as mediator, PRMQ1 as moderator
```{r}
# PHQ9 -> N300 (PRMQ1 moderator) -> Accuracy

#install.packages("mediation")
#install.packages("minqa")
#library(mediation)

model.M <- lm(N300 ~ PHQ9_c * PRMQ1_c + Gender1 + Age, data = PMD)
model.Y <- lm(Accuracy ~ N300 + PHQ9_c + Gender1 + Age, data =PMD)
results <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "PHQ9_c", 
                              mediator= 'N300', 
                              boot=TRUE, sims=10000)
summary(results)
```

## Exploratory moderated mediation!

## Using the mediate package: PHQ9 as depression, PRMQ1 mediator, N300 moderator on c' path
```{r}
# Depression -> PRMQ1 (N300 moderator) -> Accuracy
## N300 as moderator on the A path

#install.packages("mediation")
#install.packages("minqa")
library(mediation)

c <- lm(Accuracy ~ PHQ9 + Gender1 + Age, data = PMD)
summary(c)

a <- lm(PRMQ1 ~ PHQ9 + Gender1 + Age, data = PMD)
summary(a)

b <- lm(Accuracy ~ PRMQ1 + Gender1 + Age, data = PMD)
summary(b)

model.M <- lm(PRMQ1 ~ PHQ9_c + Gender1 + Age, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + PHQ9_c * N300_c + Gender1 + Age + Gender1, data =PMD)
results <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "PHQ9_c", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(results)

```
## Create APA formatted table
```{r}
# Extract effect estimates, confidence intervals, standard errors, and p-values
indirect_effect <- results$d0
indirect_ci <- c(results$d0.ci[1], results$d0.ci[2])
indirect_se <- sd(results$d0.sims)
indirect_p <- results$d0.p

direct_effect <- results$z0
direct_ci <- c(results$z0.ci[1], results$z0.ci[2])
direct_se <- sd(results$z0.sims)
direct_p <- results$z0.p

total_effect <- results$tau.coef
total_ci <- c(results$tau.ci[1], results$tau.ci[2])
total_se <- sd(results$tau.sims)
total_p <- results$tau.p

# Create data frame with all values
results_table <- data.frame(
  Effect = c("Indirect", "Direct", "Total"),
  Estimate = c(indirect_effect, direct_effect, total_effect),
  SE = c(indirect_se, direct_se, total_se),
  `CI Lower` = c(indirect_ci[1], direct_ci[1], total_ci[1]),
  `CI Upper` = c(indirect_ci[2], direct_ci[2], total_ci[2]),
  `p-value` = c(indirect_p, direct_p, total_p)
)

# install.packages("kableExtra")
# install.packages("officer")

library(officer)
library(kableExtra)

# Create APA-style table in HTML format
results_html_table <- results_table %>%
  kable("html", caption = "Model Results for PHQ-9 Relating to PM Accuracy via PM-related Metamemory  Beliefs (PRMQ) with Cue Detection as a Moderator while controlling for age and gender") %>%
  kable_styling(full_width = FALSE, position = "center") %>%
  add_header_above(c(" " = 1, "Standardized Beta" = 1, "Standard Error" = 1, "95% Confidence Interval" = 2, " " = 1)) %>%
  column_spec(2, bold = TRUE) %>%
  footnote(general = "Standardized Betas, standard errors, confidence intervals, and p-values for the indirect, direct, and total effects.",
           general_title = "Note: ")

# Create a new Word document
doc <- read_docx()

# Add the table to the Word document
doc <- doc %>%
  body_add_par("Model Results for PHQ-9 Relating to PM Accuracy via PM-related Metamemory  Beliefs (PRMQ) with Cue Detection as a Moderator while controlling for age and gender", style = "heading 1") %>%
  body_add_table(value = results_table, style = "table_template") %>%  # You can define a style template in Word if you prefer
  body_add_par("Note: Standardized Betas, standard errors, confidence intervals, and p-values for the indirect, direct, and total effects.", style = "Normal")

# Save the document
print(doc, target = "PHQ9_agegender_ModMediation_Analysis_Results.docx")

```


### Check conditional indirect effects: PHQ-9
```{r}
# Define values for the moderator (W) at mean, mean + 1 SD, and mean - 1 SD
mean_W <- mean(PMD$N300_c, na.rm = TRUE)
sd_W <- sd(PMD$N300_c, na.rm = TRUE)

W_levels <- c(mean_W, mean_W + sd_W, mean_W - sd_W)

# List to store results for each level of W
results <- list()

for (i in 1:length(W_levels)) {
  # Create a copy of the data with N300_c set to the specific level
  PMD_subset <- PMD
  PMD_subset$N300_c <- W_levels[i]
  
  # Define the mediator and outcome models
  mediator_model <- lm(PRMQ1 ~ PHQ9_c + Gender1, data = PMD_subset)
  outcome_model <- lm(Accuracy ~ PRMQ1 + PHQ9_c * N300_c + Gender1, data = PMD_subset)
  
  # Run the mediation analysis
  mediation_results <- mediation::mediate(mediator_model, 
                               outcome_model, 
                               treat = "PHQ9_c", 
                               mediator = "PRMQ1", 
                               boot = TRUE, sims = 10000)
  
  # Store the mediation results for each level
  results[[paste0("N300_c_", i)]] <- summary(mediation_results)
}

# Display the results for each level of W
results

```
### Check conditional indirect effects: CES-D
```{r}
# Define values for the moderator (W) at mean, mean + 1 SD, and mean - 1 SD
mean_W <- mean(PMD$N300_c, na.rm = TRUE)
sd_W <- sd(PMD$N300_c, na.rm = TRUE)

W_levels <- c(mean_W, mean_W + sd_W, mean_W - sd_W)

# List to store results for each level of W
results <- list()

for (i in 1:length(W_levels)) {
  # Create a copy of the data with N300_c set to the specific level
  PMD_subset <- PMD
  PMD_subset$N300_c <- W_levels[i]
  
  # Define the mediator and outcome models
  mediator_model <- lm(PRMQ1 ~ CESD_c + Gender1, data = PMD_subset)
  outcome_model <- lm(Accuracy ~ PRMQ1 + CESD_c * N300_c + Gender1, data = PMD_subset)
  
  # Run the mediation analysis
  mediation_results <- mediation::mediate(mediator_model, 
                               outcome_model, 
                               treat = "CESD_c", 
                               mediator = "PRMQ1", 
                               boot = TRUE, sims = 10000)
  
  # Store the mediation results for each level
  results[[paste0("N300_c_", i)]] <- summary(mediation_results)
}

# Display the results for each level of W
results
```

## Using the mediate package: CESD as depression, PRMQ1 mediator, N300 moderator on c' path
```{r}
c <- lm(Accuracy ~ CESD + Gender1 + Age, data = PMD)
summary(c)

a <- lm(PRMQ1 ~ CESD + Gender1 + Age, data = PMD)
summary(a)

b <- lm(Accuracy ~ PRMQ1 + Gender1 + Age, data = PMD)
summary(b)

model.M <- lm(PRMQ1 ~ CESD_c + Gender1 + Age, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + CESD_c * N300_c + Gender1 + Age, data =PMD)
results <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "CESD_c", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(results)
```

```{r}
# Extract effect estimates, confidence intervals, standard errors, and p-values
indirect_effect <- results$d0
indirect_ci <- c(results$d0.ci[1], results$d0.ci[2])
indirect_se <- sd(results$d0.sims)
indirect_p <- results$d0.p

direct_effect <- results$z0
direct_ci <- c(results$z0.ci[1], results$z0.ci[2])
direct_se <- sd(results$z0.sims)
direct_p <- results$z0.p

total_effect <- results$tau.coef
total_ci <- c(results$tau.ci[1], results$tau.ci[2])
total_se <- sd(results$tau.sims)
total_p <- results$tau.p

# Create data frame with all values
results_table <- data.frame(
  Effect = c("Indirect", "Direct", "Total"),
  Estimate = c(indirect_effect, direct_effect, total_effect),
  SE = c(indirect_se, direct_se, total_se),
  `CI Lower` = c(indirect_ci[1], direct_ci[1], total_ci[1]),
  `CI Upper` = c(indirect_ci[2], direct_ci[2], total_ci[2]),
  `p-value` = c(indirect_p, direct_p, total_p)
)

# install.packages("kableExtra")
# install.packages("officer")

library(officer)
library(kableExtra)

# Create APA-style table in HTML format
results_html_table <- results_table %>%
  kable("html", caption = "Model Results for CES-D Relating to PM Accuracy via PM-related Metamemory  Beliefs (PRMQ) with Cue Detection as a Moderator while controlling for age and gender") %>%
  kable_styling(full_width = FALSE, position = "center") %>%
  add_header_above(c(" " = 1, "Standardized Beta" = 1, "Standard Error" = 1, "95% Confidence Interval" = 2, " " = 1)) %>%
  column_spec(2, bold = TRUE) %>%
  footnote(general = "Standardized Betas, standard errors, confidence intervals, and p-values for the indirect, direct, and total effects.",
           general_title = "Note: ")

# Create a new Word document
doc <- read_docx()

# Add the table to the Word document
doc <- doc %>%
  body_add_par("Model Results for CES-D Relating to PM Accuracy via PM-related Metamemory  Beliefs (PRMQ) with Cue Detection as a Moderator while controlling for age and gender", style = "heading 1") %>%
  body_add_table(value = results_table, style = "table_template") %>%  # You can define a style template in Word if you prefer
  body_add_par("Note: Standardized Betas, standard errors, confidence intervals, and p-values for the indirect, direct, and total effects.", style = "Normal")

# Save the document
print(doc, target = "CESD_agegender_ModMediation_Analysis_Results.docx")

```




## Graph to understand N300 as a moderator on a path 
```{r}

fitInt1 <- lm(PRMQ1 ~ PHQ9_c * N300_c + Gender1 + Age, data = PMD)

interact_plot(fitInt1, pred = PHQ9_c, modx = N300_c, 
               plot.points = TRUE,    # To show individual data points
               interval = TRUE,       # To include confidence intervals
               colors = "Set1")       # Change colors if you prefer different ones

```

```{r}
model <- lm(Accuracy ~ PP + Gender1 + Age, data = PMD)
summary(model)
```


## New exploratory idea: N300 as moderator for accuracy (c' path)?------------------------------------------

### quick detour - I run N300 as a moderator for PHQ9 and accuracy.
```{r}
fit <- lm(Accuracy ~ PHQ9_c * N300_c + Gender1 + Age, data = PMD)
summary(fit)
```

### simple slopes
```{r}
library(jtools)
library(rlang)
library(interactions)

fitInt <- lm(Accuracy ~ PHQ9_c * N300_c + Gender1 + Age, data = PMD)
summary(fitInt)

sim_slopes(
  fitInt,
  PHQ9_c,
  N300_c,
  mod2 = NULL,
  modx.values = NULL,
  mod2.values = NULL,
  centered = "none",
  data = PMD,
  cond.int = FALSE,
  johnson_neyman = TRUE,
  jnplot = FALSE,
  jnalpha = 0.05,
  robust = FALSE,
  digits = getOption("jtools-digits", default = 2),
  pvals = TRUE,
  confint = FALSE,
  ci.width = 0.95)
```
### graph to understand how the N300 modated PHQ9 and accuracy (c' path)
```{r}
library(ggplot2)

fitInt <- lm(Accuracy ~ PHQ9_c * N300_c + Gender1 + Age, data = PMD)

interact_plot(fitInt, pred = PHQ9_c, modx = N300_c, 
               plot.points = TRUE,    # To show individual data points
               interval = TRUE,       # To include confidence intervals
               colors = "Set1")       # Change colors if you prefer different ones
```

## Checking other interactions
##N300 as a moderator for CESD and accuracy.
```{r}
fit <- lm(Accuracy ~ CESD_c * N300_c + Gender1 + Age, data = PMD)
summary(fit)

fit <- lm(Accuracy ~ PHQ9_c * PP_c + Gender1 + Age, data = PMD)
summary(fit)

fit <- lm(Accuracy ~ CESD_c * PP_c + Gender1 + Age, data = PMD)
summary(fit)
```
### simple slopes
```{r}
library(jtools)
library(rlang)
library(interactions)

fitInt <- lm(Accuracy ~ CESD_c * N300_c + Gender1 + Age, data = PMD)
summary(fitInt)

sim_slopes(
  fitInt,
  CESD_c,
  N300_c,
  mod2 = NULL,
  modx.values = NULL,
  mod2.values = NULL,
  centered = "none",
  data = PMD,
  cond.int = FALSE,
  johnson_neyman = TRUE,
  jnplot = FALSE,
  jnalpha = 0.05,
  robust = FALSE,
  digits = getOption("jtools-digits", default = 2),
  pvals = TRUE,
  confint = FALSE,
  ci.width = 0.95)
```

### graph to understand how the N300 modated CESD-D and accuracy (c' path)
```{r}
library(ggplot2)

fitInt <- lm(Accuracy ~ CESD_c * N300_c + Gender1 + Age, data = PMD)

interact_plot(fitInt, pred = CESD_c, modx = N300_c, 
               plot.points = TRUE,    # To show individual data points
               interval = TRUE,       # To include confidence intervals
               colors = "Set1")       # Change colors if you prefer different ones
```

# Effects sizes

## Main effects
### Partial R-squared for PHQ9 on Accuracy
```{r}
#full linear regression model
full_model <- lm(Accuracy ~ PHQ9 + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(Accuracy ~ Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

### Partial R-squared for CESD on Accuracy
```{r}
#full linear regression model
full_model <- lm(Accuracy ~ CESD + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(Accuracy ~ Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

### Partial R-squared for PHQ9 on RT
```{r}
#full linear regression model
full_model <- lm(RT ~ PHQ9 + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(RT ~ Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

### Partial R-squared for CESD on RT
```{r}
#full linear regression model
full_model <- lm(RT ~ CESD + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(RT ~ Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

### Partial R-squared for PP on RT
```{r}
#full linear regression model
full_model <- lm(RT ~ PP + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(RT ~ Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

### Partial R-squared for N300 on RT
```{r}
#full linear regression model
full_model <- lm(RT ~ N300 + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(RT ~ Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

### Partial R-squared for PP on Accuracy
```{r}
#full linear regression model
full_model <- lm(Accuracy ~ PP + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(Accuracy ~ Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

### Partial R-squared for N300 on Accuracy
```{r}
#full linear regression model
full_model <- lm(Accuracy ~ N300 + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(Accuracy ~ Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## Interactions
### Accuracy ~ PHQ9_c*N300_c
```{r}
#full linear regression model
full_model <- lm(Accuracy ~ PHQ9_c*N300_c + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(Accuracy ~ PHQ9_c + N300_c + Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

### Accuracy ~ CESD_c*N300_c
```{r}
#full linear regression model
full_model <- lm(Accuracy ~ CESD_c*N300_c + Age + Gender1, data = PMD)
# model without the predictor
reduced_model <- lm(Accuracy ~ CESD_c + N300_c + Age + Gender1, data = PMD)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

## New exploratory idea: PP as moderator for accuracy (b path)?------------------------------------------

### quick detour - I run PP as a moderator for metamemory and accuracy.
```{r}
model <- lm(Accuracy ~ PP_c*PRMQ1_c + Gender1 + Age, data = PMD)
summary(model)
```

## Metamemory as mediatior in relationship bw PP and accuracy
```{r}
# PP -> PRMQ1 -> Accuracy

#install.packages("mediation")
#install.packages("minqa")
#library(mediation)

model.M <- lm(PRMQ1 ~ PP + Gender1 + Age, data = PMD)
model.Y <- lm(Accuracy ~ PRMQ1 + PP + Gender1 + Age, data =PMD)
results <- mediation::mediate(model.M, 
                              model.Y, 
                              treat =  "PP", 
                              mediator= 'PRMQ1', 
                              boot=TRUE, sims=10000)
summary(results)
```
## New exploratory idea: PP as moderator for accuracy (c' path)?------------------------------------------

### quick detour - I run PP as a moderator for metamemory and accuracy.
```{r}
model <- lm(Accuracy ~ PP_c * PHQ9_c + Gender1 + Age, data = PMD)
summary(model)
```
# Per Deana's request: isolate how N300 and PP look for PM in normal population and depressed populations
```{r}

# Low depression subset
low_dep <- PMD[PMD$PHQ9 <= 3, ]

# High depression subset
high_dep <- PMD[PMD$PHQ9 >= 10, ]

# Check the results
describe(low_dep)

describe(high_dep)

# N300 and accuracy in low depression
model <- lm(Accuracy ~ scale(N300) + Age + Gender1, data = low_dep)
summary(model)

# PP and accuracy in low depression
model1 <- lm(Accuracy ~ scale(PP) + Age + Gender1, data = low_dep)
summary(model1)

# N300 and accuracy in high depression
model2 <- lm(Accuracy ~ scale(N300) + Age + Gender1, data = high_dep)
summary(model2)

# PP and accuracy in high depression
model3 <- lm(Accuracy ~ scale(PP) + Age + Gender1, data = high_dep)
summary(model3)

model4 <- lm(Accuracy ~ scale(PP) + Age + Gender1, data = PMD)
summary(model4)

model5 <- lm(Accuracy ~ scale(N300) + Age + Gender1, data = PMD)
summary(model5)

```
```{r}
 # Paired t-test
t_test_result <- t.test(high_dep$N300, low_dep$N300, paired = FALSE)

# View the result
print(t_test_result)
```



